\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}

\geometry{a4paper, margin=1in}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}

\title{\Huge Optimization Model for SCRUM-Based Software Development \\ \Large Based on Domain Entities and Relationships}
\author{\Large AI Assistant \\ \normalsize Knowledge-Based Modeling System}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{1. Sets (Entities)}
\item $ \mathcal{P} $: Set of Projects, $ P \in \mathcal{P} $, with attributes: id, name, project\_start, project\_end, description, budget, status, target\_audience, priority.
    \item $ \mathcal{T} $: Set of Teams, $ T \in \mathcal{T} $, with attributes: id, name, team\_size, team\_start, team\_status, location, team\_type.
    \item $ \mathcal{W} $: Set of Workers, $ W \in \mathcal{W} $, with attributes: id, name, first\_name, email, start\_date, status, availability.
    \item $ \mathcal{F} $: Set of Features, $ F \in \mathcal{F} $, with attributes: id, title, description, status, priority, estimated\_effort.
    \item $ \mathcal{S} $: Set of Skills, $ S \in \mathcal{S} $, with attributes: id, label, description, level, certified, category.
    \item $ \mathcal{R} $: Set of Roles, $ R \in \mathcal{R} $, with attributes: id, role\_name, description, area\_of\_responsibility.
    \item $ \mathcal{PO} $: Set of Product Owners, $ PO \in \mathcal{PO} $, with attributes: id, name, email, availability.
    \item $ \mathcal{SM} $: Set of Scrum Masters, $ SM \in \mathcal{SM} $, with attributes: id, name, email, experience.
    \item $ \mathcal{PB} $: Set of Product Backlogs, $ PB \in \mathcal{PB} $, with attributes: id, created\_on, last\_updated, number\_of\_entries, status.
    \item $ \mathcal{SP} $: Set of Sprints, $ SP \in \mathcal{SP} $, with attributes: id, sprint\_number, start\_date, end\_date, status, achievement\_of\_goal.
    \item $ \mathcal{SPP} $: Set of Sprint Plannings, $ SPP \in \mathcal{SPP} $, with attributes: id, date, duration\_(min), moderation, outcome\_documentation.
    \item $ \mathcal{DS} $: Set of Daily Scrums, $ DS \in \mathcal{DS} $, with attributes: id, date, time, duration, moderation.
    \item $ \mathcal{SR} $: Set of Sprint Reviews, $ SR \in \mathcal{SR} $, with attributes: id, date, duration, feedback\_documentation, attendees\_count.
    \item $ \mathcal{SRE} $: Set of Sprint Retrospectives, $ SRE \in \mathcal{SRE} $, with attributes: id, date, duration, improvement\_actions, team\_satisfaction, moderation.
    \item $ \mathcal{SBL} $: Set of Sprint Backlogs, $ SBL \in \mathcal{SBL} $, with attributes: id, number\_of\_tasks, last\_updated, status, total\_effort.
    \item $ \mathcal{SG} $: Set of Sprint Goals, $ SG \in \mathcal{SG} $, with attributes: id, objective\_description, achievement\_status, benefit.
    \item $ \mathcal{E} $: Set of Epics, $ E \in \mathcal{E} $, with attributes: id, title, description, priority, status, estimated\_effort.
    \item $ \mathcal{US} $: Set of User Stories, $ US \in \mathcal{US} $, with attributes: id, title, description, acceptance\_criteria, priority, story\_points, status.
    \item $ \mathcal{TSK} $: Set of Tasks, $ TSK \in \mathcal{TSK} $, with attributes: id, title, description, status, effort, type.
    \item $ \mathcal{DEV} $: Set of Development Snapshots, $ DEV \in \mathcal{DEV} $, with attributes: id, version\_number, creation\_date, test\_status, deployment\_target, documentation.
    \item $ \mathcal{BL} $: Set of Blockers, $ BL \in \mathcal{BL} $, with attributes: id, title, description, severity, status, detected\_on, resolved\_on.
    \item $ \mathcal{SH} $: Set of Stakeholders, $ SH \in \mathcal{SH} $, with attributes: id, name, organization, role, email, area\_of\_interest, influence\_level, relevance\_to\_feature.
    \item $ \mathcal{VEL} $: Set of Velocity Records, $ VEL \in \mathcal{VEL} $, with attributes: id, number\_of\_sprints\_used, avg.\_story\_points, max\_velocity, min\_velocity, trend.
    \item $ \mathcal{REP} $: Set of Release Plans, $ REP \in \mathcal{REP} $, with attributes: id, version, planned\_date, included\_features, status.
    \item $ \mathcal{RM} $: Set of Roadmaps, $ RM \in \mathcal{RM} $, with attributes: id, start\_date, end\_date, milestones, objectives, versions.
    \item $ \mathcal{SCB} $: Set of Scrum Boards, $ SCB \in \mathcal{SCB} $, with attributes: id, board\_type, columns\_(todo/done...), number\_of\_cards, last\_updated.
    \item $ \mathcal{FED} $: Set of Feature Documentations, $ FED \in \mathcal{FED} $, with attributes: id, title, description, creation\_date, change\_log, linked\_requirements, author.

\section{2. Indices}
\item $ p \in \mathcal{P} $: Index for Projects.
    \item $ t \in \mathcal{T} $: Index for Teams.
    \item $ w \in \mathcal{W} $: Index for Workers.
    \item $ f \in \mathcal{F} $: Index for Features.
    \item $ s \in \mathcal{S} $: Index for Skills.
    \item $ r \in \mathcal{R} $: Index for Roles.
    \item $ sp \in \mathcal{SP} $: Index for Sprints.
    \item $ us \in \mathcal{US} $: Index for User Stories.
    \item $ tk \in \mathcal{TSK} $: Index for Tasks.
    \item $ bl \in \mathcal{BL} $: Index for Blockers.
    \item $ sh \in \mathcal{SH} $: Index for Stakeholders.
    \item $ v \in \mathcal{VEL} $: Index for Velocity records.
    \item $ rp \in \mathcal{REP} $: Index for Release Plans.
    \item $ rm \in \mathcal{RM} $: Index for Roadmaps.

\section{3. Goals}
\item \textbf{G0: maximize\_project\_budget} \\
    Maximize total budget across selected projects: \\
    $ \max \sum_{p \in \mathcal{P}} x_p \cdot \text{budget}(p) $

    \item \textbf{G1: minimize\_project\_duration} \\
    Minimize total project duration: \\
    $ \min \sum_{p \in \mathcal{P}} x_p \cdot (\text{project\_end}(p) - \text{project\_start}(p)) $

    \item \textbf{G2: maximize\_team\_size} \\
    Maximize cumulative team size: \\
    $ \max \sum_{t \in \mathcal{T}} y_t \cdot \text{team\_size}(t) $

    \item \textbf{G3: minimize\_worker\_start\_date} \\
    Prefer earlier-starting workers: \\
    $ \min \sum_{w \in \mathcal{W}} z_w \cdot \text{start\_date}(w) $

    \item \textbf{G4: maximize\_worker\_availability} \\
    Maximize total worker availability: \\
    $ \max \sum_{w \in \mathcal{W}} z_w \cdot \text{availability}(w) $

    \item \textbf{G5: maximize\_feature\_priority} \\
    Maximize sum of feature priorities: \\
    $ \max \sum_{f \in \mathcal{F}} u_f \cdot \text{priority}(f) $

    \item \textbf{G6: minimize\_task\_effort} \\
    Minimize total task effort: \\
    $ \min \sum_{tk \in \mathcal{TSK}} v_{tk} \cdot \text{effort}(tk) $

    \item \textbf{G7: maximize\_story\_points} \\
    Maximize completed story points: \\
    $ \max \sum_{us \in \mathcal{US}} v_{us} \cdot \text{story\_points}(us) $

    \item \textbf{G8: minimize\_sprint\_duration} \\
    Minimize sprint length: \\
    $ \min \sum_{sp \in \mathcal{SP}} w_{sp} \cdot (\text{end\_date}(sp) - \text{start\_date}(sp)) $

    \item \textbf{G9: maximize\_sprint\_achievement} \\
    Maximize sprint goal achievement: \\
    $ \max \sum_{sp \in \mathcal{SP}} w_{sp} \cdot \text{achievement\_of\_goal}(sp) $

    \item \textbf{G10: minimize\_blocker\_resolution\_time} \\
    Minimize average blocker resolution time: \\
    $ \min \sum_{bl \in \mathcal{BL}} b_{bl} \cdot (\text{resolved\_on}(bl) - \text{detected\_on}(bl)) $

    \item \textbf{G11: maximize\_velocity\_trend} \\
    Maximize velocity trend: \\
    $ \max \sum_{v \in \mathcal{VEL}} a_v \cdot \text{trend}(v) $

    \item \textbf{G12: maximize\_stakeholder\_influence} \\
    Maximize influence of involved stakeholders: \\
    $ \max \sum_{sh \in \mathcal{SH}} c_{sh} \cdot \text{influence\_level}(sh) $

    \item \textbf{G13: minimize\_release\_plan\_delay} \\
    Minimize release plan dates: \\
    $ \min \sum_{rp \in \mathcal{REP}} d_{rp} \cdot \text{planned\_date}(rp) $

    \item \textbf{G14: maximize\_epic\_effort\_estimate} \\
    Maximize effort allocated to epics: \\
    $ \max \sum_{e \in \mathcal{E}} e_e \cdot \text{estimated\_effort}(e) $

\section{4. Conditions}
\item \textbf{C0: require\_project\_status\_active} \\
    Only active projects are allowed: \\
    $ x_p = 1 \implies \text{status}(p) = \text{``active''}, \quad \forall p \in \mathcal{P} $

    \item \textbf{C1: require\_team\_status\_active} \\
    Only active teams can be assigned: \\
    $ y_t = 1 \implies \text{team\_status}(t) = \text{``active''}, \quad \forall t \in \mathcal{T} $

    \item \textbf{C2: require\_worker\_status\_active} \\
    Only active workers can be allocated: \\
    $ z_w = 1 \implies \text{status}(w) = \text{``active''}, \quad \forall w \in \mathcal{W} $

    \item \textbf{C3: require\_feature\_status\_completed} \\
    Only completed features contribute: \\
    $ u_f > 0 \implies \text{status}(f) = \text{``completed''}, \quad \forall f \in \mathcal{F} $

    \item \textbf{C4: require\_task\_status\_done} \\
    Only done tasks are considered: \\
    $ v_{tk} = 1 \implies \text{status}(tk) = \text{``done''}, \quad \forall tk \in \mathcal{TSK} $

    \item \textbf{C5: require\_sprint\_status\_completed} \\
    Only completed sprints count: \\
    $ w_{sp} = 1 \implies \text{status}(sp) = \text{``completed''}, \quad \forall sp \in \mathcal{SP} $

    \item \textbf{C6: require\_valid\_role\_assignment} \\
    Worker must have at least one valid role: \\
    $ z_w = 1 \implies \exists r \in \mathcal{R} : \text{takes\_on\_role}(w,r), \quad \forall w \in \mathcal{W} $

    \item \textbf{C7: require\_certified\_skills} \\
    Only certified skills are used: \\
    $ \text{has\_skill}(w,s) \implies \text{certified}(s) = \text{true}, \quad \forall w \in \mathcal{W}, s \in \mathcal{S} $

    \item \textbf{C8: require\_non\_zero\_story\_points} \\
    Exclude zero-point stories: \\
    $ v_{us} = 1 \implies \text{story\_points}(us) > 0, \quad \forall us \in \mathcal{US} $

    \item \textbf{C9: require\_positive\_effort} \\
    Task effort must be positive: \\
    $ v_{tk} = 1 \implies \text{effort}(tk) > 0, \quad \forall tk \in \mathcal{TSK} $

    \item \textbf{C10: require\_valid\_sprint\_goal} \\
    Sprint must have defined goal: \\
    $ w_{sp} = 1 \implies \exists sg \in \mathcal{SG} : \text{pursues\_goal}(sp, sg) \land \text{objective\_description}(sg) \neq \emptyset $

    \item \textbf{C11: require\_documented\_feature} \\
    Feature must have documentation: \\
    $ u_f = 1 \implies \exists fed \in \mathcal{FED} : \text{documents\_feature}(fed,f), \quad \forall f \in \mathcal{F} $

    \item \textbf{C12: require\_planned\_release\_status} \\
    Release must be planned or released: \\
    $ d_{rp} = 1 \implies \text{status}(rp) \in \{\text{``planned''}, \text{``released''}\}, \quad \forall rp \in \mathcal{REP} $

    \item \textbf{C13: require\_roadmap\_milestone\_defined} \\
    Roadmap must have at least one milestone: \\
    $ \text{is\_part\_of\_roadmap}(rp, rm) \implies \text{milestones}(rm) \neq \emptyset, \quad \forall rp \in \mathcal{REP}, rm \in \mathcal{RM} $

    \item \textbf{C14: require\_non\_empty\_backlog} \\
    Product Backlog must contain items: \\
    $ \text{contains\_feature}(pb,f) \lor \text{contains\_epic}(pb,e) \implies \text{number\_of\_entries}(pb) > 0, \quad \forall pb \in \mathcal{PB} $

\section{5. DecisionVariables}
\item $ x_p \in \{0,1\} $: Project selection variable for $ p \in \mathcal{P} $
    \item $ y_t \in [1,10] $: Number of teams assigned to a project (continuous)
    \item $ z_w \in [0,1] $: Worker allocation level for $ w \in \mathcal{W} $
    \item $ s_{tk,s} \in \{1,2,3,4,5\} $: Minimum required skill level for task $ tk $
    \item $ r_w \in [1,3] $: Number of roles assigned to worker $ w $
    \item $ u_f \in [1,10] $: Priority score for feature $ f $
    \item $ d_{sp} \in [5,30] $: Duration (in days) of sprint $ sp $
    \item $ v_{tk} \in \{0,1\} $: Task completion status (1 if done)
    \item $ v_{us} \in [1,20] $: Estimated story points for user story $ us $
    \item $ b_{bl} \in \{1,2,3\} $: Blocker severity level for $ bl \in \mathcal{BL} $
    \item $ c_{sh} \in [0,1] $: Stakeholder influence weight
    \item $ m_v \in [0.5, 2.0] $: Velocity multiplier for team performance prediction
    \item $ v_{rp} \in [1.0, 10.0] $: Release version number
    \item $ f_{fed} \in [0, 100] $: Documentation completeness percentage
    \item $ n_{scb} \in [3,7] $: Number of columns on Scrum Board $ scb $

\end{document}