\documentclass{article}
\title{Optimization Model}
\author{Dolphin}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section*{1. Sets (Entities)}
\begin{itemize}
    \item Project: $P = \{p_0, p_1, ..., p_n\}$
    \item Team: $T = \{t_0, t_1, ..., t_m\}$
    \item Worker: $W = \{w_0, w_1, ..., w_k\}$
    \item Feature: $F = \{f_0, f_1, ..., f_l\}$
    \item Skill: $S = \{s_0, s_1, ..., s_p\}$
    \item Role: $R = \{r_0, r_1, ..., r_q\}$
    \item Product Owner: $PO = \{po_0, po_1, ..., po_r\}$
    \item Scrum Master: $SM = \{sm_0, sm_1, ..., sm_s\}$
    \item Product Backlog: $PB = \{pb_0, pb_1, ..., pb_t\}$
    \item Sprint: $SP = \{sp_0, sp_1, ..., sp_v\}$
    \item User Story: $US = \{us_0, us_1, ..., us_w\}$
    \item Task: $TSK = \{tsk_0, tsk_1, ..., tsk_x\}$
    \item Development Snapshot: $DEV = \{dev_0, dev_1, ..., dev_y\}$
    \item Blocker: $BL = \{bl_0, bl_1, ..., bl_z\}$
    \item Stakeholder: $SH = \{sh_0, sh_1, ..., sh_aa\}$
    \item Velocity: $VEL = \{vel_0, vel_1, ..., vel_bb\}$
    \item Release Plan: $REP = \{rep_0, rep_1, ..., rep_cc\}$
    \item Roadmap: $RM = \{rm_0, rm_1, ..., rm_dd\}$
    \item Scrum Board: $SCB = \{scb_0, scb_1, ..., scb_e\}$
    \item Feature Documentation: $FED = \{fed_0, fed_1, ..., fed_ff\}$
\end{itemize}

\section*{2. Indices}
\begin{itemize}
    \item $i$: Index of Projects
    \item $j$: Index of Teams
    \item $k$: Index of Workers
    \item $l$: Index of Features
    \item $m$: Index of Skills
    \item $n$: Index of Roles
    \item $r$: Index of Product Owners
    \item $s$: Index of Scrum Masters
    \item $t$: Index of Product Backlogs
    \item $u$: Index of Epics
    \item $v$: Index of Sprints
    \item $w$: Index of User Stories
    \item $x$: Index of Tasks
    \item $y$: Index of Development Snapshots
    \item $z$: Index of Blockers
    \item $aa$: Index of Stakeholders
    \item $bb$: Index of Velocities
    \item $cc$: Index of Release Plans
    \item $dd$: Index of Roadmaps
    \item $e$: Index of Scrum Boards
\end{itemize}

\section*{3. Goals}
\begin{itemize}
    \item $G0$: Maximize the profit of projects.
        \[
        max_{i} Profit_i
        \]
    \item $G1$: Minimize the cost of developing projects.
        \[
        min_{i} Cost_i
        \]
    \item $G2$: Maximize team efficiency.
        \[
        max_{j} Efficiency_j
        \]
    \item $G3$: Minimize project duration.
        \[
        min_{i} Duration_i
        \]
    \item $G4$: Maximize worker satisfaction.
        \[
        max_{k} Satisfaction_k
        \]
    \item $G5$: Minimize worker unavailability.
        \[
        min_{k} Unavailability_k
        \]
\end{itemize}

\section*{4. Conditions}
\begin{itemize}
    \item $C0$: Project budget must not exceed the allocated budget.
        \[
        0 \leq Budget_i \leq AllocatedBudget
        \]
    \item $C1$: Each sprint should last for a maximum of two weeks.
        \[
        Duration_{SP_u} \leq 120 \quad \forall u
        \]
    \item $C2$: The team size must not exceed twenty members.
        \[
        Size_j \leq 20 \quad \forall j
        \]
    \item $C3$: Each worker must have sufficient skills to complete their tasks.
        \[
        Skill_k \geq RequiredSkill \quad \forall k
        \]
\end{itemize}

\section*{5. DecisionVariables}
\begin{itemize}
    \item $D0$: Select a team for a project.
    \item $D1$: Set the length of a sprint in minutes.
    \item $D2$: Choose the start date for a sprint.
\end{itemize}

\end{document}