\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, graphicx, hyperref, enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{datetime2}

\title{Optimization Model for SCRUM-Based Software Development}
\author{Domain Modeling and Optimization Team}
\date{\DTMtoday}

\begin{document}

\maketitle

\tableofcontents
\newpage

\section{1. Sets (Entities)}

This section defines the core entities (sets) in the SCRUM domain model.

\item $ \mathcal{P} $: Set of Projects, where each $ p \in \mathcal{P} $ has attributes: id, name, project\_start, project\_end, description, budget, status, target\_audience, priority.
    \item $ \mathcal{T} $: Set of Teams, where each $ t \in \mathcal{T} $ has attributes: id, name, team\_size, team\_start, team\_status, location, team\_type.
    \item $ \mathcal{W} $: Set of Workers, where each $ w \in \mathcal{W} $ has attributes: id, name, first\_name, email, start\_date, status, availability.
    \item $ \mathcal{F} $: Set of Features, where each $ f \in \mathcal{F} $ has attributes: id, title, description, status, priority, estimated\_effort.
    \item $ \mathcal{S} $: Set of Skills, where each $ s \in \mathcal{S} $ has attributes: id, label, description, level, certified, category.
    \item $ \mathcal{R} $: Set of Roles, where each $ r \in \mathcal{R} $ has attributes: id, role\_name, description, area\_of\_responsibility.
    \item $ \mathcal{PO} $: Set of Product Owners, where each $ po \in \mathcal{PO} $ has attributes: id, name, email, availability.
    \item $ \mathcal{SM} $: Set of Scrum Masters, where each $ sm \in \mathcal{SM} $ has attributes: id, name, email, experience.
    \item $ \mathcal{PB} $: Set of Product Backlogs, where each $ pb \in \mathcal{PB} $ has attributes: id, created\_on, last\_updated, number\_of\_entries, status.
    \item $ \mathcal{SP} $: Set of Sprints, where each $ sp \in \mathcal{SP} $ has attributes: id, sprint\_number, start\_date, end\_date, status, achievement\_of\_goal.
    \item $ \mathcal{SPP} $: Set of Sprint Plannings, where each $ spp \in \mathcal{SPP} $ has attributes: id, date, duration\_(min), moderation, outcome\_documentation.
    \item $ \mathcal{DS} $: Set of Daily Scrums, where each $ ds \in \mathcal{DS} $ has attributes: id, date, time, duration, moderation.
    \item $ \mathcal{SR} $: Set of Sprint Reviews, where each $ sr \in \mathcal{SR} $ has attributes: id, date, duration, feedback\_documentation, attendees\_count.
    \item $ \mathcal{SRE} $: Set of Sprint Retrospectives, where each $ sre \in \mathcal{SRE} $ has attributes: id, date, duration, improvement\_actions, team\_satisfaction, moderation.
    \item $ \mathcal{SBL} $: Set of Sprint Backlogs, where each $ sbl \in \mathcal{SBL} $ has attributes: id, number\_of\_tasks, last\_updated, status, total\_effort.
    \item $ \mathcal{SG} $: Set of Sprint Goals, where each $ sg \in \mathcal{SG} $ has attributes: id, objective\_description, achievement\_status, benefit.
    \item $ \mathcal{E} $: Set of Epics, where each $ e \in \mathcal{E} $ has attributes: id, title, description, priority, status, estimated\_effort.
    \item $ \mathcal{US} $: Set of User Stories, where each $ us \in \mathcal{US} $ has attributes: id, title, description, acceptance\_criteria, priority, story\_points, status.
    \item $ \mathcal{TSK} $: Set of Tasks, where each $ tsk \in \mathcal{TSK} $ has attributes: id, title, description, status, effort, type.
    \item $ \mathcal{DEV} $: Set of Development Snapshots, where each $ dev \in \mathcal{DEV} $ has attributes: id, version\_number, creation\_date, test\_status, deployment\_target, documentation.
    \item $ \mathcal{BL} $: Set of Blockers, where each $ bl \in \mathcal{BL} $ has attributes: id, title, description, severity, status, detected\_on, resolved\_on.
    \item $ \mathcal{SH} $: Set of Stakeholders, where each $ sh \in \mathcal{SH} $ has attributes: id, name, organization, role, email, area\_of\_interest, influence\_level, relevance\_to\_feature.
    \item $ \mathcal{VEL} $: Set of Velocity Records, where each $ vel \in \mathcal{VEL} $ has attributes: id, number\_of\_sprints\_used, avg.\_story\_points, max\_velocity, min\_velocity, trend.
    \item $ \mathcal{REP} $: Set of Release Plans, where each $ rep \in \mathcal{REP} $ has attributes: id, version, planned\_date, included\_features, status.
    \item $ \mathcal{RM} $: Set of Roadmaps, where each $ rm \in \mathcal{RM} $ has attributes: id, start\_date, end\_date, milestones, objectives, versions.
    \item $ \mathcal{SCB} $: Set of Scrum Boards, where each $ scb \in \mathcal{SCB} $ has attributes: id, board\_type, columns\_(todo/done...), number\_of\_cards, last\_updated.
    \item $ \mathcal{FED} $: Set of Feature Documentations, where each $ fed \in \mathcal{FED} $ has attributes: id, title, description, creation\_date, change\_log, linked\_requirements, author.

\section{2. Indices}

Indices are used to reference elements within the defined sets.

\item $ p \in \mathcal{P} $: Index for a specific Project.
    \item $ t \in \mathcal{T} $: Index for a specific Team.
    \item $ w \in \mathcal{W} $: Index for a specific Worker.
    \item $ f \in \mathcal{F} $: Index for a specific Feature.
    \item $ s \in \mathcal{S} $: Index for a specific Skill.
    \item $ r \in \mathcal{R} $: Index for a specific Role.
    \item $ po \in \mathcal{PO} $: Index for a Product Owner.
    \item $ sm \in \mathcal{SM} $: Index for a Scrum Master.
    \item $ pb \in \mathcal{PB} $: Index for a Product Backlog.
    \item $ sp \in \mathcal{SP} $: Index for a Sprint.
    \item $ spp \in \mathcal{SPP} $: Index for a Sprint Planning session.
    \item $ ds \in \mathcal{DS} $: Index for a Daily Scrum.
    \item $ sr \in \mathcal{SR} $: Index for a Sprint Review.
    \item $ sre \in \mathcal{SRE} $: Index for a Sprint Retrospective.
    \item $ sbl \in \mathcal{SBL} $: Index for a Sprint Backlog.
    \item $ sg \in \mathcal{SG} $: Index for a Sprint Goal.
    \item $ e \in \mathcal{E} $: Index for an Epic.
    \item $ us \in \mathcal{US} $: Index for a User Story.
    \item $ tsk \in \mathcal{TSK} $: Index for a Task.
    \item $ dev \in \mathcal{DEV} $: Index for a Development Snapshot.
    \item $ bl \in \mathcal{BL} $: Index for a Blocker.
    \item $ sh \in \mathcal{SH} $: Index for a Stakeholder.
    \item $ vel \in \mathcal{VEL} $: Index for a Velocity record.
    \item $ rep \in \mathcal{REP} $: Index for a Release Plan.
    \item $ rm \in \mathcal{RM} $: Index for a Roadmap.
    \item $ scb \in \mathcal{SCB} $: Index for a Scrum Board.
    \item $ fed \in \mathcal{FED} $: Index for Feature Documentation.

\section{3. Goals}

Optimization objectives, each with logical and mathematical representation.

\item \textbf{G0: maximize\_project\_budget} \\
    \textit{Logical:} Maximize the total budget of all active projects. \\
    \textit{Mathematical:} $ \max \sum_{p \in \mathcal{P}} \text{budget}(p) \cdot \mathbb{I}_{\text{status}(p) = \text{active}} \times 1.5 $

    \item \textbf{G1: maximize\_team\_size} \\
    \textit{Logical:} Maximize the sum of team sizes across all teams. \\
    \textit{Mathematical:} $ \max \sum_{t \in \mathcal{T}} \text{team\_size}(t) \times 1.0 $

    \item \textbf{G2: maximize\_worker\_availability} \\
    \textit{Logical:} Maximize the sum of availability scores of all workers. \\
    \textit{Mathematical:} $ \max \sum_{w \in \mathcal{W}} \text{availability}(w) \times 1.2 $

    \item \textbf{G3: minimize\_feature\_estimated\_effort} \\
    \textit{Logical:} Minimize the total estimated effort for all features. \\
    \textit{Mathematical:} $ \min \sum_{f \in \mathcal{F}} \text{estimated\_effort}(f) \times 0.8 $

    \item \textbf{G4: maximize\_user\_story\_story\_points} \\
    \textit{Logical:} Maximize the sum of story points of all user stories in the sprint backlog. \\
    \textit{Mathematical:} $ \max \sum_{us \in \mathcal{US}} \text{story\_points}(us) \cdot x_{us} \times 1.3 $, where $ x_{us} = 1 $ if assigned to sprint.

    \item \textbf{G5: minimize\_sprint\_duration} \\
    \textit{Logical:} Minimize the duration between sprint start and end. \\
    \textit{Mathematical:} $ \min (\text{end\_date}(sp) - \text{start\_date}(sp)) \times 1.0 $

    \item \textbf{G6: maximize\_sprint\_achievement\_of\_goal} \\
    \textit{Logical:} Maximize the average goal achievement across sprints. \\
    \textit{Mathematical:} $ \max \frac{1}{|\mathcal{SP}|} \sum_{sp \in \mathcal{SP}} \text{achievement\_of\_goal}(sp) \times 1.6 $

    \item \textbf{G7: minimize\_blocker\_severity} \\
    \textit{Logical:} Minimize the average severity of unresolved blockers. \\
    \textit{Mathematical:} $ \min \frac{1}{|\mathcal{BL}|} \sum_{bl \in \mathcal{BL}} \text{severity}(bl) \cdot \mathbb{I}_{\text{status}(bl) \neq \text{resolved}} \times 0.9 $

    \item \textbf{G8: maximize\_velocity\_avg\_story\_points} \\
    \textit{Logical:} Maximize the average story points delivered per sprint. \\
    \textit{Mathematical:} $ \max \text{avg.\_story\_points}(vel) \times 1.7 $ for $ vel \in \mathcal{VEL} $

    \item \textbf{G9: minimize\_task\_effort} \\
    \textit{Logical:} Minimize the total effort of all tasks in the current sprint. \\
    \textit{Mathematical:} $ \min \sum_{tsk \in \mathcal{TSK}} \text{effort}(tsk) \cdot y_{tsk} \times 0.7 $, where $ y_{tsk} = 1 $ if task is active.

    \item \textbf{G10: maximize\_sprint\_review\_attendees} \\
    \textit{Logical:} Maximize the number of attendees in sprint reviews. \\
    \textit{Mathematical:} $ \max \sum_{sr \in \mathcal{SR}} \text{attendees\_count}(sr) \times 1.1 $

    \item \textbf{G11: minimize\_sprint\_planning\_duration} \\
    \textit{Logical:} Minimize the duration of sprint planning meetings. \\
    \textit{Mathematical:} $ \min \text{duration\_(min)}(spp) \times 0.6 $

    \item \textbf{G12: maximize\_team\_satisfaction} \\
    \textit{Logical:} Maximize team satisfaction in retrospectives. \\
    \textit{Mathematical:} $ \max \text{team\_satisfaction}(sre) \times 1.4 $

    \item \textbf{G13: minimize\_release\_plan\_delay} \\
    \textit{Logical:} Minimize deviation from planned release dates. \\
    \textit{Mathematical:} $ \min \left| \text{actual\_date}(rep) - \text{planned\_date}(rep) \right| \times 0.8 $

    \item \textbf{G14: maximize\_number\_of\_features\_released} \\
    \textit{Logical:} Maximize the count of features included in release plans. \\
    \textit{Mathematical:} $ \max \sum_{rep \in \mathcal{REP}} |\text{included\_features}(rep)| \times 1.3 $

\section{4. Conditions}

Constraints and filtering rules applied to the model.

\item \textbf{C0: require\_project\_status\_active} \\
    \textit{Logical:} Only projects with status "active" are considered. \\
    \textit{Mathematical:} $ \forall p \in \mathcal{P},\ \text{status}(p) = \text{active} $

    \item \textbf{C1: require\_team\_status\_active} \\
    \textit{Logical:} Only teams with status "active" are eligible. \\
    \textit{Mathematical:} $ \forall t \in \mathcal{T},\ \text{team\_status}(t) = \text{active} $

    \item \textbf{C2: require\_worker\_status\_active} \\
    \textit{Logical:} Only workers with status "active" can be assigned. \\
    \textit{Mathematical:} $ \forall w \in \mathcal{W},\ \text{status}(w) = \text{active} $

    \item \textbf{C3: require\_feature\_status\_not\_done} \\
    \textit{Logical:} Features must not be in "done" status. \\
    \textit{Mathematical:} $ \forall f \in \mathcal{F},\ \text{status}(f) \neq \text{done} $

    \item \textbf{C4: require\_user\_story\_status\_todo} \\
    \textit{Logical:} Only user stories with status "To Do" are assignable. \\
    \textit{Mathematical:} $ \forall us \in \mathcal{US},\ \text{status}(us) = \text{To Do} $

    \item \textbf{C5: require\_task\_status\_not\_blocked} \\
    \textit{Logical:} Tasks must not have status "blocked". \\
    \textit{Mathematical:} $ \forall tsk \in \mathcal{TSK},\ \text{status}(tsk) \neq \text{blocked} $

    \item \textbf{C6: require\_blocker\_status\_resolved} \\
    \textit{Logical:} Only resolved blockers are archived; active ones must be addressed. \\
    \textit{Mathematical:} $ \forall bl \in \mathcal{BL},\ \text{status}(bl) = \text{resolved} \Rightarrow \text{resolved\_on}(bl) \leq \text{current\_date} $

    \item \textbf{C7: require\_sprint\_status\_active} \\
    \textit{Logical:} Only active sprints are valid for assignment. \\
    \textit{Mathematical:} $ \forall sp \in \mathcal{SP},\ \text{status}(sp) = \text{active} $

    \item \textbf{C8: require\_sprint\_goal\_achievement\_pending} \\
    \textit{Logical:} Sprint goal must not be marked as achieved yet. \\
    \textit{Mathematical:} $ \forall sg \in \mathcal{SG},\ \text{achievement\_status}(sg) = \text{pending} $

    \item \textbf{C9: require\_skill\_certified} \\
    \textit{Logical:} Only certified skills are valid for role assignment. \\
    \textit{Mathematical:} $ \forall s \in \mathcal{S},\ \text{certified}(s) = \text{true} $

    \item \textbf{C10: require\_role\_area\_defined} \\
    \textit{Logical:} Role must have a defined area of responsibility. \\
    \textit{Mathematical:} $ \forall r \in \mathcal{R},\ \text{area\_of\_responsibility}(r) \neq \emptyset $

    \item \textbf{C11: require\_product\_backlog\_status\_open} \\
    \textit{Logical:} Only open backlogs can be modified. \\
    \textit{Mathematical:} $ \forall pb \in \mathcal{PB},\ \text{status}(pb) = \text{open} $

    \item \textbf{C12: require\_velocity\_trend\_positive} \\
    \textit{Logical:} Prefer teams with positive velocity trend. \\
    \textit{Mathematical:} $ \forall vel \in \mathcal{VEL},\ \text{trend}(vel) \geq 0 $

    \item \textbf{C13: require\_release\_plan\_status\_active} \\
    \textit{Logical:} Only active release plans are considered. \\
    \textit{Mathematical:} $ \forall rep \in \mathcal{REP},\ \text{status}(rep) = \text{active} $

    \item \textbf{C14: require\_roadmap\_milestones\_defined} \\
    \textit{Logical:} All roadmaps must have at least one milestone. \\
    \textit{Mathematical:} $ \forall rm \in \mathcal{RM},\ \text{milestones}(rm) \neq \emptyset $

\section{5. DecisionVariables}

Variables that can be adjusted during optimization.

\item $ dv_0 \in \mathbb{Z} $: \texttt{project\_priority\_assignment}, domain $ \{1,2,3,4,5\} $, $ 1 \leq dv_0 \leq 5 $
    \item $ dv_1 \in \mathbb{R} $: \texttt{team\_assignment\_weight}, continuous, $ 0.0 \leq dv_1 \leq 1.0 $
    \item $ dv_2 \in \mathbb{R} $: \texttt{worker\_availability\_score}, $ 0.0 \leq dv_2 \leq 100.0 $
    \item $ dv_3 \in \mathbb{Z} $: \texttt{feature\_priority}, domain $ \{1,2,3\} $, $ 1 \leq dv_3 \leq 3 $
    \item $ dv_4 \in \mathbb{Z} $: \texttt{user\_story\_priority}, domain $ \{1,2,3\} $, $ 1 \leq dv_4 \leq 3 $
    \item $ dv_5 \in \mathbb{Z} $: \texttt{task\_effort\_estimate}, in hours, $ 1 \leq dv_5 \leq 40 $
    \item $ dv_6 \in \mathbb{Z} $: \texttt{sprint\_duration\_days}, $ 5 \leq dv_6 \leq 30 $
    \item $ dv_7 \in \mathbb{Z} $: \texttt{planning\_meeting\_duration}, in minutes, $ 60 \leq dv_7 \leq 180 $
    \item $ dv_8 \in \mathbb{Z} $: \texttt{daily\_scrum\_duration}, $ 10 \leq dv_8 \leq 30 $
    \item $ dv_9 \in \mathbb{R} $: \texttt{retrospective\_moderation\_score}, $ 1.0 \leq dv_9 \leq 5.0 $
    \item $ dv_{10} \in \mathbb{Z} $: \texttt{blocker\_severity\_level}, domain $ \{1,2,3\} $, $ 1 \leq dv_{10} \leq 3 $
    \item $ dv_{11} \in \mathbb{Z} $: \texttt{velocity\_calculation\_window}, number of sprints, $ 1 \leq dv_{11} \leq 10 $
    \item $ dv_{12} \in \mathbb{R} $: \texttt{release\_version\_number}, interpreted as float, $ 1.0 \leq dv_{12} \leq 3.0 $
    \item $ dv_{13} \in \mathbb{Z} $: \texttt{roadmap\_start\_year}, $ 2023 \leq dv_{13} \leq 2030 $
    \item $ dv_{14} \in \mathbb{R} $: \texttt{documentation\_completion\_status}, percentage, $ 0.0 \leq dv_{14} \leq 100.0 $

\end{document}