\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}

\geometry{margin=1in}
\titleformat{\section}{\large\bfseries}{}{0em}{}[{\titlerule[0.5pt]}]
\titleformat{\subsection}{\bfseries}{}{0em}{}

\title{\Huge Optimization Model for a Scrum-Based Software Development Company \\ \vspace{0.5cm} \Large Mathematical Formulation}
\author{\textbf{Domain Modeling and Optimization Team}}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{1. Sets (Entities)}
\item $\mathcal{P}$: Set of Projects, where each $p \in \mathcal{P}$ has attributes: id, name, project\_start, project\_end, description, budget, status, target\_audience, priority.
    \item $\mathcal{T}$: Set of Teams, where each $t \in \mathcal{T}$ has attributes: id, name, team\_size, team\_start, team\_status, location, team\_type.
    \item $\mathcal{W}$: Set of Workers, where each $w \in \mathcal{W}$ has attributes: id, name, first\_name, email, start\_date, status, availability.
    \item $\mathcal{F}$: Set of Features, where each $f \in \mathcal{F}$ has attributes: id, title, description, status, priority, estimated\_effort.
    \item $\mathcal{S}$: Set of Skills, where each $s \in \mathcal{S}$ has attributes: id, label, description, level, certified, category.
    \item $\mathcal{R}$: Set of Roles, where each $r \in \mathcal{R}$ has attributes: id, role\_name, description, area\_of\_responsibility.
    \item $\mathcal{PO}$: Set of Product Owners, where each $po \in \mathcal{PO}$ has attributes: id, name, email, availability.
    \item $\mathcal{SM}$: Set of Scrum Masters, where each $sm \in \mathcal{SM}$ has attributes: id, name, email, experience.
    \item $\mathcal{PB}$: Set of Product Backlogs, where each $pb \in \mathcal{PB}$ has attributes: id, created\_on, last\_updated, number\_of\_entries, status.
    \item $\mathcal{SP}$: Set of Sprints, where each $sp \in \mathcal{SP}$ has attributes: id, sprint\_number, start\_date, end\_date, status, achievement\_of\_goal.
    \item $\mathcal{SPP}$: Set of Sprint Plannings, where each $spp \in \mathcal{SPP}$ has attributes: id, date, duration\_in\_min, moderation, outcome\_documentation.
    \item $\mathcal{DS}$: Set of Daily Scrums, where each $ds \in \mathcal{DS}$ has attributes: id, date, time, duration, moderation.
    \item $\mathcal{SR}$: Set of Sprint Reviews, where each $sr \in \mathcal{SR}$ has attributes: id, date, duration, feedback\_documentation, attendees\_count.
    \item $\mathcal{SRE}$: Set of Sprint Retrospectives, where each $sre \in \mathcal{SRE}$ has attributes: id, date, duration, improvement\_actions, team\_satisfaction, moderation.
    \item $\mathcal{SBL}$: Set of Sprint Backlogs, where each $sbl \in \mathcal{SBL}$ has attributes: id, number\_of\_tasks, last\_updated, status, total\_effort.
    \item $\mathcal{SG}$: Set of Sprint Goals, where each $sg \in \mathcal{SG}$ has attributes: id, objective\_description, achievement\_status, benefit.
    \item $\mathcal{E}$: Set of Epics, where each $e \in \mathcal{E}$ has attributes: id, title, description, priority, status, estimated\_effort.
    \item $\mathcal{US}$: Set of User Stories, where each $us \in \mathcal{US}$ has attributes: id, title, description, acceptance\_criteria, priority, story\_points, status.
    \item $\mathcal{TSK}$: Set of Tasks, where each $tsk \in \mathcal{TSK}$ has attributes: id, title, description, status, effort, type.
    \item $\mathcal{DEV}$: Set of Development Snapshots, where each $dev \in \mathcal{DEV}$ has attributes: id, version\_number, creation\_date, test\_status, deployment\_target, documentation.
    \item $\mathcal{BL}$: Set of Blockers, where each $bl \in \mathcal{BL}$ has attributes: id, title, description, severity, status, detected\_on, resolved\_on.
    \item $\mathcal{SH}$: Set of Stakeholders, where each $sh \in \mathcal{SH}$ has attributes: id, name, organization, role, email, area\_of\_interest, influence\_level, relevance\_to\_feature.
    \item $\mathcal{VEL}$: Set of Velocity Records, where each $vel \in \mathcal{VEL}$ has attributes: id, number\_of\_sprints\_used, avg.\_story\_points, max\_velocity, min\_velocity, trend.
    \item $\mathcal{REP}$: Set of Release Plans, where each $rep \in \mathcal{REP}$ has attributes: id, version, planned\_date, included\_features, status.
    \item $\mathcal{RM}$: Set of Roadmaps, where each $rm \in \mathcal{RM}$ has attributes: id, start\_date, end\_date, milestones, objectives, versions.
    \item $\mathcal{SCB}$: Set of Scrum Boards, where each $scb \in \mathcal{SCB}$ has attributes: id, board\_type, columns\_(todo/done...), number\_of\_cards, last\_updated.
    \item $\mathcal{FED}$: Set of Feature Documentations, where each $fed \in \mathcal{FED}$ has attributes: id, title, description, creation\_date, change\_log, linked\_requirements, author.

\section{2. Indices}
\item $p \in \mathcal{P}$: Index for projects.
    \item $t \in \mathcal{T}$: Index for teams.
    \item $w \in \mathcal{W}$: Index for workers.
    \item $f \in \mathcal{F}$: Index for features.
    \item $s \in \mathcal{S}$: Index for skills.
    \item $r \in \mathcal{R}$: Index for roles.
    \item $sp \in \mathcal{SP}$: Index for sprints.
    \item $us \in \mathcal{US}$: Index for user stories.
    \item $tsk \in \mathcal{TSK}$: Index for tasks.
    \item $bl \in \mathcal{BL}$: Index for blockers.
    \item $sh \in \mathcal{SH}$: Index for stakeholders.
    \item $vel \in \mathcal{VEL}$: Index for velocity records.
    \item $rep \in \mathcal{REP}$: Index for release plans.

\section{3. Goals}
\item \textbf{G0: maximize\_project\_budget} \\
    Maximize total project budget: 
    \[
    \max \sum_{p \in \mathcal{P}} \text{budget}(p) \quad \text{with weight } 1.5
    \]

    \item \textbf{G1: minimize\_project\_duration} \\
    Minimize total duration across projects:
    \[
    \min \sum_{p \in \mathcal{P}} \left( \text{project\_end}(p) - \text{project\_start}(p) \right) \quad \text{with weight } 1.2
    \]

    \item \textbf{G2: maximize\_team\_size} \\
    Maximize total team capacity:
    \[
    \max \sum_{t \in \mathcal{T}} \text{team\_size}(t) \quad \text{with weight } 0.8
    \]

    \item \textbf{G3: minimize\_worker\_unavailability} \\
    Minimize number of inactive workers:
    \[
    \min \sum_{w \in \mathcal{W}} \mathbb{I}[\text{status}(w) \neq \text{active}] \quad \text{with weight } 1.0
    \]

    \item \textbf{G4: maximize\_feature\_priority} \\
    Maximize sum of feature priorities:
    \[
    \max \sum_{f \in \mathcal{F}} \text{priority}(f) \quad \text{with weight } 1.3
    \]

    \item \textbf{G5: minimize\_task\_effort} \\
    Minimize total task effort:
    \[
    \min \sum_{tsk \in \mathcal{TSK}} \text{effort}(tsk) \quad \text{with weight } 1.1
    \]

    \item \textbf{G6: maximize\_story\_points} \\
    Maximize total story points:
    \[
    \max \sum_{us \in \mathcal{US}} \text{story\_points}(us) \quad \text{with weight } 1.4
    \]

    \item \textbf{G7: minimize\_sprint\_duration} \\
    Minimize sprint length:
    \[
    \min \sum_{sp \in \mathcal{SP}} \left( \text{end\_date}(sp) - \text{start\_date}(sp) \right) \quad \text{with weight } 0.9
    \]

    \item \textbf{G8: maximize\_velocity\_trend} \\
    Maximize velocity trend:
    \[
    \max \sum_{vel \in \mathcal{VEL}} \text{trend}(vel) \quad \text{with weight } 1.6
    \]

    \item \textbf{G9: minimize\_blocker\_severity} \\
    Minimize total blocker severity:
    \[
    \min \sum_{bl \in \mathcal{BL}} \text{severity}(bl) \quad \text{with weight } 1.3
    \]

    \item \textbf{G10: maximize\_stakeholder\_influence} \\
    Maximize sum of stakeholder influence:
    \[
    \max \sum_{sh \in \mathcal{SH}} \text{influence\_level}(sh) \quad \text{with weight } 1.0
    \]

    \item \textbf{G11: minimize\_epic\_estimated\_effort} \\
    Minimize total epic effort:
    \[
    \min \sum_{e \in \mathcal{E}} \text{estimated\_effort}(e) \quad \text{with weight } 1.1
    \]

    \item \textbf{G12: maximize\_sprint\_achievement} \\
    Maximize average sprint goal achievement:
    \[
    \max \frac{1}{|\mathcal{SP}|} \sum_{sp \in \mathcal{SP}} \text{achievement\_of\_goal}(sp) \quad \text{with weight } 1.5
    \]

    \item \textbf{G13: minimize\_documentation\_age} \\
    Minimize age of documentation (inverse of creation date):
    \[
    \min \sum_{fed \in \mathcal{FED}} \left( T - \text{creation\_date}(fed) \right) \quad \text{(T = current date), weight } 0.7
    \]

    \item \textbf{G14: maximize\_release\_plan\_inclusion} \\
    Maximize number of features in release plans:
    \[
    \max \sum_{rep \in \mathcal{REP}} |\text{included\_features}(rep)| \quad \text{with weight } 1.2
    \]

\section{4. Conditions}
\item \textbf{C0: require\_project\_status\_active} \\
    Only active projects are considered:
    \[
    \forall p \in \mathcal{P}: \text{status}(p) = \text{active}
    \]

    \item \textbf{C1: require\_team\_status\_active} \\
    Only active teams:
    \[
    \forall t \in \mathcal{T}: \text{team\_status}(t) = \text{active}
    \]

    \item \textbf{C2: require\_worker\_status\_active} \\
    Only active workers:
    \[
    \forall w \in \mathcal{W}: \text{status}(w) = \text{active}
    \]

    \item \textbf{C3: require\_feature\_status\_completed} \\
    Only completed features:
    \[
    \forall f \in \mathcal{F}: \text{status}(f) = \text{completed} \Rightarrow \text{include in goals}
    \]

    \item \textbf{C4: require\_user\_story\_status\_done} \\
    Only done user stories:
    \[
    \forall us \in \mathcal{US}: \text{status}(us) = \text{done}
    \]

    \item \textbf{C5: require\_task\_status\_not\_blocked} \\
    Tasks must not be blocked:
    \[
    \forall tsk \in \mathcal{TSK}: \text{status}(tsk) \neq \text{blocked}
    \]

    \item \textbf{C6: require\_sprint\_status\_completed} \\
    Only completed sprints:
    \[
    \forall sp \in \mathcal{SP}: \text{status}(sp) = \text{completed}
    \]

    \item \textbf{C7: require\_blocker\_status\_resolved} \\
    All blockers must be resolved:
    \[
    \forall bl \in \mathcal{BL}: \text{status}(bl) = \text{resolved}
    \]

    \item \textbf{C8: require\_skill\_certified} \\
    Skills must be certified:
    \[
    \forall s \in \mathcal{S}: \text{certified}(s) = \text{true}
    \]

    \item \textbf{C9: require\_role\_assigned} \\
    Each worker must have at least one role:
    \[
    \forall w \in \mathcal{W}, \exists r \in \mathcal{R}: (w, r) \in \text{takes\_on\_role}
    \]

    \item \textbf{C10: require\_velocity\_min\_value} \\
    Minimum velocity must be positive:
    \[
    \forall vel \in \mathcal{VEL}: \text{min\_velocity}(vel) > 0
    \]

    \item \textbf{C11: require\_release\_status\_planned} \\
    Only planned releases:
    \[
    \forall rep \in \mathcal{REP}: \text{status}(rep) = \text{planned}
    \]

    \item \textbf{C12: require\_roadmap\_milestones\_defined} \\
    Roadmaps must have milestones:
    \[
    \forall rm \in \mathcal{RM}: \text{milestones}(rm) \neq \emptyset
    \]

    \item \textbf{C13: require\_daily\_scrum\_held} \\
    Daily scrum must occur each day of sprint:
    \[
    \forall sp \in \mathcal{SP}, \forall d \in [\text{start\_date}(sp), \text{end\_date}(sp)]: \exists ds \in \mathcal{DS} \mid \text{date}(ds) = d
    \]

    \item \textbf{C14: require\_sprint\_goal\_defined} \\
    Every sprint must have a goal:
    \[
    \forall sp \in \mathcal{SP}, \exists sg \in \mathcal{SG}: \text{pursues\_goal}(sp, sg) \land \text{objective\_description}(sg) \neq \emptyset
    \]

\section{5. DecisionVariables}
\item \texttt{project\_priority\_weight}: Weight applied to project priority ranking, $ \in [0.0, 10.0] $.
    \item \texttt{team\_size\_capacity}: Maximum number of workers per team, $ \in \mathbb{Z}, [1, 20] $.
    \item \texttt{worker\_availability\_hours}: Weekly availability per worker, $ \in \mathbb{Z}, [0, 40] $.
    \item \texttt{task\_effort\_estimate}: Estimated effort for a task in hours, $ \in \mathbb{Z}, [1, 160] $.
    \item \texttt{user\_story\_points}: Story points assigned to a user story, $ \in \{1, 2, 3, 5, 8, 13\} $.
    \item \texttt{sprint\_duration\_days}: Duration of a sprint in days, $ \in \{7, 14, 21, 28\} $.
    \item \texttt{blocker\_severity\_level}: Severity level of a blocker, $ \in \{1, 2, 3\} $.
    \item \texttt{feature\_priority\_score}: Priority score of a feature, $ \in \mathbb{Z}, [1, 10] $.
    \item \texttt{velocity\_avg\_story\_points}: Average story points per sprint, $ \in \mathbb{R}, [0.0, 100.0] $.
    \item \texttt{stakeholder\_influence\_level}: Influence level of a stakeholder, $ \in \mathbb{Z}, [0, 5] $.
    \item \texttt{release\_version\_number}: Version number for a release, $ \in \mathbb{R}, [1.0, 10.0] $.
    \item \texttt{documentation\_change\_count}: Number of changes in documentation, $ \in \mathbb{Z}, [0, 100] $.
    \item \texttt{scrum\_board\_column\_count}: Number of columns on a Scrum Board, $ \in \mathbb{Z}, [2, 6] $.
    \item \texttt{task\_type\_category}: Type of task, $ \in \{\text{development}, \text{testing}, \text{bug\_fix}, \text{documentation}\} $.
    \item \texttt{skill\_level\_rating}: Skill proficiency level, $ \in \{1, 2, 3, 4, 5\} $.

\end{document}