\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

\title{Software Development Optimization Model}
\date{}
\maketitle

\section{Introduction}
This document presents a mathematical model for optimizing the software development process, based on the provided entities, relationships, goals, and conditions.

\section{Sets}
\begin{itemize}
    \item $T$: Set of Teams
    \item $S$: Set of Sprints
    \item $U$: Set of User Stories
    \item $F$: Set of Features
    \item $B$: Set of Blockers/Bugs
\end{itemize}

\section{Parameters}
\begin{itemize}
    \item $v_t$: Velocity of Team $t$ (derived from historical data).
    \item $w_f$: Importance weight of Feature $f$ (based on stakeholder input).
    \item $c_b$: Severity cost of Bug $b$ (based on impact assessment).
    \item $max\_capacity\_s$: Maximum Story Point capacity for Sprint $s$.
\end{itemize}

\section{Decision Variables}
\begin{itemize}
    \item $x_t$: Team Size for team $t$ (Numeric, Domain: [3, 10]).
    \item $y_s$: Sprint Length for sprint $s$ (Numeric, Domain: [14, 28] days).
    \item $z_u$: Story Point Estimate for user story $u$ (Numeric).
    \item $a_u$: Binary variable: 1 if user story $u$ is allocated to a sprint, 0 otherwise.
    \item $b_t$: Binary variable: 1 if team $t$ is assigned to a bug, 0 otherwise.
    \item $c_s$: Sprint Goal Focus for sprint $s$ (Numeric, Domain [0,1]).
    \item $d_f$: Documentation Effort for feature $f$ (Numeric).
\end{itemize}

\section{Objective Function}

Maximize:

\[
\sum_{f \in F} w_f + \sum_{t \in T} v_t x_t + \sum_{s \in S} c_s - \sum_{b \in B} c_b  - \sum_{f \in F} d_f
\]

\section{Constraints}

\begin{enumerate}
    \item Capacity Constraint (per Sprint):
    \[
    \sum_{u \in U} z_u a_u \leq max\_capacity\_s \quad \forall s \in S
    \]
    \item Team Size Constraint:
    \[
    3 \leq x_t \leq 10 \quad \forall t \in T
    \]
    \item Sprint Length Constraint:
    \[
    14 \leq y_s \leq 28 \quad \forall s \in S
    \]
    \item Bug Assignment Constraint:
    \[
    \sum_{t \in T} b_t \leq |B|
    \]
    \item Documentation Time Constraint:
    \[
    d_f \geq 0 \quad \forall f \in F
    \]
    \item Allocation Constraint:
    \[
    a_u \in \{0, 1\} \quad \forall u \in U
    \]
\end{enumerate}

\end{document}