\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}

\title{Optimization Model for Agile Software Development}
\author{AI Assistant}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}
This document outlines an optimization model for agile software development, considering various factors such as team size, sprint velocity, and project budget. The model aims to maximize project success while adhering to constraints and objectives.

\section{Sets (Entities)}
\begin{itemize}
    \item \textbf{Teams}: Represents the development teams.
    \item \textbf{Projects}: Represents the software projects.
    \item \textbf{Features}: Represents the features to be implemented.
    \item \textbf{Epics}: Represents large bodies of work.
    \item \textbf{Stories}: Represents user stories.
    \item \textbf{Tasks}: Represents individual tasks within stories.
    \item \textbf{Blockers}: Represents obstacles hindering progress.
    \item \textbf{Workers}: Represents team members.
    \item \textbf{Releases}: Represents software releases.
    \item \textbf{Stakeholders}: Represents individuals with interest in the project.
\end{itemize}

\section{Indices}
\begin{itemize}
    \item $i$: Index for Teams
    \item $j$: Index for Projects
    \item $k$: Index for Features
    \item $l$: Index for Epics
    \item $m$: Index for Stories
    \item $n$: Index for Tasks
    \item $o$: Index for Blockers
\end{itemize}

\section{Goals}
\begin{itemize}
    \item \textbf{G0: maximize\_team\_size}: Maximize the number of teams.
    \item \textbf{G1: maximize\_sprint\_velocity}: Maximize the sprint velocity.
    \item \textbf{G2: minimize\_blocker\_count}: Minimize the number of blockers.
    \item \textbf{G3: maximize\_feature\_completion}: Maximize the number of completed features.
    \item \textbf{G4: maximize\_epic\_coverage}: Maximize the number of epic covered by stories.
\end{itemize}

\section{Conditions}
\begin{itemize}
    \item \textbf{C0: must\_have\_team}: Ensure each project has an assigned team.
    \item \textbf{C1: must\_have\_scrum\_master}: Ensure each team has a dedicated Scrum Master.
    \item \textbf{C2: must\_have\_product\_owner}: Ensure each project has a Product Owner.
    \item \textbf{C3: must\_meet\_budget}: Ensure project stays within budget.
    \item \textbf{C4: must\_have\_valid\_status}: Ensure feature status is valid.
\end{itemize}

\section{DecisionVariables}
\begin{itemize}
    \item \textbf{DV0: team\_size}: Number of team members.
    \item \textbf{DV1: sprint\_duration}: Duration of the sprint in days.
    \item \textbf{DV2: story\_point\_estimate}: Estimate of story points per sprint.
    \item \textbf{DV3: blocker\_resolution\_time}: Time to resolve a blocker in hours.
    \item \textbf{DV4: feature\_development\_time}: Time to develop a feature in days.
\end{itemize}

\end{document}