\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, graphicx, hyperref, enumitem}
\usepackage[margin=1in]{geometry}
\title{Optimization Model for SCRUM-Based Software Development}
\author{Domain Modeling and Optimization Team}
\date{\today}
\begin{document}

\maketitle

\tableofcontents
\newpage

\section{1. Sets (Entities)}
\item $\mathcal{P}$: Set of Projects, where each $p \in \mathcal{P}$ has attributes: id, name, project\_start, project\_end, description, budget, status, target\_audience, priority.
    \item $\mathcal{T}$: Set of Teams, where each $t \in \mathcal{T}$ has attributes: id, name, team\_size, team\_start, team\_status, location, team\_type.
    \item $\mathcal{W}$: Set of Workers, where each $w \in \mathcal{W}$ has attributes: id, name, first\_name, email, start\_date, status, availability.
    \item $\mathcal{F}$: Set of Features, where each $f \in \mathcal{F}$ has attributes: id, title, description, status, priority, estimated\_effort.
    \item $\mathcal{S}$: Set of Skills, where each $s \in \mathcal{S}$ has attributes: id, label, description, level, certified, category.
    \item $\mathcal{R}$: Set of Roles, where each $r \in \mathcal{R}$ has attributes: id, role\_name, description, area\_of\_responsibility.
    \item $\mathcal{PO}$: Set of Product Owners, where each $po \in \mathcal{PO}$ has attributes: id, name, email, availability.
    \item $\mathcal{SM}$: Set of Scrum Masters, where each $sm \in \mathcal{SM}$ has attributes: id, name, email, experience.
    \item $\mathcal{PB}$: Set of Product Backlogs, where each $pb \in \mathcal{PB}$ has attributes: id, created\_on, last\_updated, number\_of\_entries, status.
    \item $\mathcal{SP}$: Set of Sprints, where each $sp \in \mathcal{SP}$ has attributes: id, sprint\_number, start\_date, end\_date, status, achievement\_of\_goal.
    \item $\mathcal{SPP}$: Set of Sprint Plannings, where each $spp \in \mathcal{SPP}$ has attributes: id, date, duration\_(min), moderation, outcome\_documentation.
    \item $\mathcal{DS}$: Set of Daily Scrums, where each $ds \in \mathcal{DS}$ has attributes: id, date, time, duration, moderation.
    \item $\mathcal{SR}$: Set of Sprint Reviews, where each $sr \in \mathcal{SR}$ has attributes: id, date, duration, feedback\_documentation, attendees\_count.
    \item $\mathcal{SRE}$: Set of Sprint Retrospectives, where each $sre \in \mathcal{SRE}$ has attributes: id, date, duration, improvement\_actions, team\_satisfaction, moderation.
    \item $\mathcal{SBL}$: Set of Sprint Backlogs, where each $sbl \in \mathcal{SBL}$ has attributes: id, number\_of\_tasks, last\_updated, status, total\_effort.
    \item $\mathcal{SG}$: Set of Sprint Goals, where each $sg \in \mathcal{SG}$ has attributes: id, objective\_description, achievement\_status, benefit.
    \item $\mathcal{E}$: Set of Epics, where each $e \in \mathcal{E}$ has attributes: id, title, description, priority, status, estimated\_effort.
    \item $\mathcal{US}$: Set of User Stories, where each $us \in \mathcal{US}$ has attributes: id, title, description, acceptance\_criteria, priority, story\_points, status.
    \item $\mathcal{TSK}$: Set of Tasks, where each $tsk \in \mathcal{TSK}$ has attributes: id, title, description, status, effort, type.
    \item $\mathcal{DEV}$: Set of Development Snapshots, where each $dev \in \mathcal{DEV}$ has attributes: id, version\_number, creation\_date, test\_status, deployment\_target, documentation.
    \item $\mathcal{BL}$: Set of Blockers, where each $bl \in \mathcal{BL}$ has attributes: id, title, description, severity, status, detected\_on, resolved\_on.
    \item $\mathcal{SH}$: Set of Stakeholders, where each $sh \in \mathcal{SH}$ has attributes: id, name, organization, role, email, area\_of\_interest, influence\_level, relevance\_to\_feature.
    \item $\mathcal{VEL}$: Set of Velocity Records, where each $vel \in \mathcal{VEL}$ has attributes: id, number\_of\_sprints\_used, avg.\_story\_points, max\_velocity, min\_velocity, trend.
    \item $\mathcal{REP}$: Set of Release Plans, where each $rep \in \mathcal{REP}$ has attributes: id, version, planned\_date, included\_features, status.
    \item $\mathcal{RM}$: Set of Roadmaps, where each $rm \in \mathcal{RM}$ has attributes: id, start\_date, end\_date, milestones, objectives, versions.
    \item $\mathcal{SCB}$: Set of Scrum Boards, where each $scb \in \mathcal{SCB}$ has attributes: id, board\_type, columns\_(todo/done...), number\_of\_cards, last\_updated.
    \item $\mathcal{FED}$: Set of Feature Documentations, where each $fed \in \mathcal{FED}$ has attributes: id, title, description, creation\_date, change\_log, linked\_requirements, author.

\section{2. Indices}
\item $p \in \mathcal{P}$: Index for projects.
    \item $t \in \mathcal{T}$: Index for teams.
    \item $w \in \mathcal{W}$: Index for workers.
    \item $f \in \mathcal{F}$: Index for features.
    \item $s \in \mathcal{S}$: Index for skills.
    \item $r \in \mathcal{R}$: Index for roles.
    \item $sp \in \mathcal{SP}$: Index for sprints.
    \item $us \in \mathcal{US}$: Index for user stories.
    \item $tsk \in \mathcal{TSK}$: Index for tasks.
    \item $bl \in \mathcal{BL}$: Index for blockers.
    \item $sh \in \mathcal{SH}$: Index for stakeholders.
    \item $vel \in \mathcal{VEL}$: Index for velocity records.
    \item $rep \in \mathcal{REP}$: Index for release plans.
    \item $rm \in \mathcal{RM}$: Index for roadmaps.

\section{3. Goals}
\item \textbf{G0: maximize\_project\_budget} \\
    Maximize total budget of active projects. \\
    $\max \sum_{p \in \mathcal{P}} \text{budget}_p \cdot \mathbb{I}(\text{status}_p = \text{active})$ \\
    Weight: 1.5

    \item \textbf{G1: minimize\_project\_duration} \\
    Minimize total project duration (end - start). \\
    $\min \sum_{p \in \mathcal{P}} (\text{project\_end}_p - \text{project\_start}_p)$ \\
    Weight: 1.3

    \item \textbf{G2: maximize\_team\_size} \\
    Maximize sum of team sizes. \\
    $\max \sum_{t \in \mathcal{T}} \text{team\_size}_t$ \\
    Weight: 1.0

    \item \textbf{G3: minimize\_worker\_start\_date} \\
    Minimize average worker start date (earlier = more experienced). \\
    $\min \frac{1}{|\mathcal{W}|} \sum_{w \in \mathcal{W}} \text{start\_date}_w$ \\
    Weight: 0.9

    \item \textbf{G4: maximize\_worker\_availability} \\
    Maximize total worker availability (as percentage). \\
    $\max \sum_{w \in \mathcal{W}} \text{availability}_w$ \\
    Weight: 1.2

    \item \textbf{G5: maximize\_feature\_priority} \\
    Maximize sum of feature priorities. \\
    $\max \sum_{f \in \mathcal{F}} \text{priority}_f$ \\
    Weight: 1.4

    \item \textbf{G6: minimize\_sprint\_duration} \\
    Minimize average sprint duration. \\
    $\min \frac{1}{|\mathcal{SP}|} \sum_{sp \in \mathcal{SP}} (\text{end\_date}_{sp} - \text{start\_date}_{sp})$ \\
    Weight: 1.1

    \item \textbf{G7: maximize\_sprint\_achievement} \\
    Maximize average sprint goal achievement. \\
    $\max \frac{1}{|\mathcal{SP}|} \sum_{sp \in \mathcal{SP}} \text{achievement\_of\_goal}_{sp}$ \\
    Weight: 1.6

    \item \textbf{G8: maximize\_story\_points} \\
    Maximize total completed story points. \\
    $\max \sum_{us \in \mathcal{US}} \text{story\_points}_{us} \cdot \mathbb{I}(\text{status}_{us} = \text{done})$ \\
    Weight: 1.3

    \item \textbf{G9: minimize\_task\_effort} \\
    Minimize effort spent on tasks blocked by high-severity issues. \\
    $\min \sum_{tsk \in \mathcal{TSK}} \text{effort}_{tsk} \cdot \mathbb{I}(\exists bl \in \mathcal{BL}: \text{severity}_{bl} = \text{high} \land \text{status}_{bl} = \text{open})$ \\
    Weight: 0.8

    \item \textbf{G10: maximize\_velocity\_trend} \\
    Maximize positive velocity trend. \\
    $\max \sum_{vel \in \mathcal{VEL}} \text{trend}_{vel}$ \\
    Weight: 1.5

    \item \textbf{G11: minimize\_number\_of\_blockers} \\
    Minimize number of open blockers. \\
    $\min \sum_{bl \in \mathcal{BL}} \mathbb{I}(\text{status}_{bl} = \text{open})$ \\
    Weight: 1.2

    \item \textbf{G12: maximize\_documentation\_coverage} \\
    Maximize number of features with linked documentation. \\
    $\max \sum_{f \in \mathcal{F}} \mathbb{I}(\exists fed \in \mathcal{FED}: \text{linked\_requirements}_{fed} \ni f)$ \\
    Weight: 1.0

    \item \textbf{G13: minimize\_release\_delay} \\
    Minimize total delay in release plans. \\
    $\min \sum_{rep \in \mathcal{REP}} \max(0, \text{current\_date} - \text{planned\_date}_{rep})$ \\
    Weight: 1.1

    \item \textbf{G14: maximize\_stakeholder\_influence} \\
    Maximize sum of influence levels of stakeholders involved in reviews. \\
    $\max \sum_{sh \in \mathcal{SH}} \text{influence\_level}_{sh} \cdot \mathbb{I}(sh \text{ participated in sprint review})$ \\
    Weight: 1.0

\section{4. Conditions}
\item \textbf{C0: required\_project\_status} \\
    All considered projects must be active. \\
    $\forall p \in \mathcal{P}: \text{status}_p = \text{active}$ \\
    CriteriaType: Must-Match (2), Weight: 1.0

    \item \textbf{C1: forbidden\_worker\_status} \\
    Workers must not be inactive. \\
    $\forall w \in \mathcal{W}: \text{status}_w \neq \text{inactive}$ \\
    CriteriaType: Cannot-Match (0), Weight: 0.9

    \item \textbf{C2: required\_team\_status} \\
    Teams must be active. \\
    $\forall t \in \mathcal{T}: \text{team\_status}_t = \text{active}$ \\
    CriteriaType: Must-Match (2), Weight: 1.0

    \item \textbf{C3: required\_feature\_status} \\
    Features must be in progress or done. \\
    $\forall f \in \mathcal{F}: \text{status}_f \in \{\text{in progress}, \text{done}\}$ \\
    CriteriaType: Must-Match (2), Weight: 1.2

    \item \textbf{C4: forbidden\_task\_status} \\
    Tasks cannot be cancelled. \\
    $\forall tsk \in \mathcal{TSK}: \text{status}_{tsk} \neq \text{cancelled}$ \\
    CriteriaType: Cannot-Match (0), Weight: 0.8

    \item \textbf{C5: required\_sprint\_status} \\
    Sprints must be active or completed. \\
    $\forall sp \in \mathcal{SP}: \text{status}_{sp} \in \{\text{active}, \text{completed}\}$ \\
    CriteriaType: Must-Match (2), Weight: 1.1

    \item \textbf{C6: required\_user\_story\_status} \\
    User stories must not be rejected. \\
    $\forall us \in \mathcal{US}: \text{status}_{us} \neq \text{rejected}$ \\
    CriteriaType: Must-Match (2), Weight: 1.0

    \item \textbf{C7: required\_skill\_certification} \\
    Skills used must be certified. \\
    $\forall s \in \mathcal{S}: \text{certified}_s = \text{true}$ \\
    CriteriaType: Must-Match (2), Weight: 1.3

    \item \textbf{C8: required\_role\_area} \\
    Roles must be in development or QA. \\
    $\forall r \in \mathcal{R}: \text{area\_of\_responsibility}_r \in \{\text{development}, \text{QA}\}$ \\
    CriteriaType: May-Match (1), Weight: 0.9

    \item \textbf{C9: required\_blocker\_severity} \\
    Only high or medium severity blockers are considered. \\
    $\forall bl \in \mathcal{BL}: \text{severity}_{bl} \in \{\text{high}, \text{medium}\}$ \\
    CriteriaType: Must-Match (2), Weight: 1.1

    \item \textbf{C10: required\_snapshot\_test\_status} \\
    Development snapshots must pass testing. \\
    $\forall dev \in \mathcal{DEV}: \text{test\_status}_{dev} = \text{passed}$ \\
    CriteriaType: Must-Match (2), Weight: 1.0

    \item \textbf{C11: required\_planned\_release} \\
    Releases must be in planned status. \\
    $\forall rep \in \mathcal{REP}: \text{status}_{rep} = \text{planned}$ \\
    CriteriaType: Must-Match (2), Weight: 0.9

    \item \textbf{C12: required\_roadmap\_milestones} \\
    Roadmaps must have defined milestones. \\
    $\forall rm \in \mathcal{RM}: \text{milestones}_{rm} \neq \emptyset$ \\
    CriteriaType: Must-Match (2), Weight: 1.0

    \item \textbf{C13: required\_board\_update} \\
    Scrum boards must be updated within the last 24 hours. \\
    $\forall scb \in \mathcal{SCB}: \text{last\_updated}_{scb} \geq \text{current\_time} - 24\text{h}$ \\
    CriteriaType: Must-Match (2), Weight: 0.8

    \item \textbf{C14: required\_stakeholder\_relevance} \\
    Stakeholders must be relevant to current feature. \\
    $\forall sh \in \mathcal{SH}: \text{relevance\_to\_feature}_{sh} = \text{high}$ \\
    CriteriaType: Must-Match (2), Weight: 1.1

\section{5. Decision Variables}
\item $x_p \in [0.0, 1.0]$: \texttt{project\_priority\_weight} — Priority weight assigned to project $p$.
    \item $y_t \in \{0,1,2,3,4\}$: \texttt{team\_allocation\_count} — Number of teams assigned to a project.
    \item $l_w \in [0.0, 1.0]$: \texttt{worker\_load\_percentage} — Fraction of full-time capacity assigned to current sprint.
    \item $d_{sp} \in \{5,10,14,21,30\}$: \texttt{sprint\_length\_days} — Duration of sprint $sp$ in calendar days.
    \item $r_{tsk} \in \{1,2,3,4,5\}$: \texttt{task\_priority\_rank} — Priority rank of task $tsk$.
    \item $e_f \in \{1,2,3,5,8,13\}$: \texttt{feature\_estimated\_effort} — Estimated effort (in story points) for feature $f$.
    \item $v_{rep} \in \{1.0, 2.0, 3.0, 4.0, 5.0\}$: \texttt{planned\_release\_version} — Version number for release plan $rep$.
    \item $c_{fed} \in [0.0, 1.0]$: \texttt{documentation\_completeness} — Completeness score of feature documentation $fed$.
    \item $t_{bl} \in \{1,2,3,5,7,14\}$: \texttt{blocker\_resolution\_time} — Expected resolution time (days) for blocker $bl$.
    \item $v_{vel} \in \{5,10,15,20,25,30\}$: \texttt{velocity\_prediction} — Forecasted velocity (story points) for next sprint.
    \item $m_{evt} \in \{15,30,60,90,120\}$: \texttt{meeting\_duration\_minutes} — Duration of Scrum event (e.g., planning, retrospective).
    \item $s_w \in \{1,2,3,4,5\}$: \texttt{worker\_skill\_level} — Skill level of worker $w$ (1=Junior, 5=Expert).
    \item $sat_{sre} \in \{1,2,3,4,5\}$: \texttt{retrospective\_satisfaction} — Team satisfaction score from retrospective $sre$.
    \item $a_{sg} \in [0.0, 1.0]$: \texttt{goal\_achievement\_score} — Measured achievement of sprint goal $sg$.
    \item $I_f \in \{0,1\}$: \texttt{feature\_inclusion\_flag} — Binary indicator if feature $f$ is included in next release.

\end{document}