\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{setspace}

\geometry{margin=1in}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlength{\parindent}{0pt}
\onehalfspacing

\title{\Huge Optimization Model for Scrum-Based Software Development \\ \Large Domain-Driven Mathematical Formulation}
\author{\Large AI Assistant \\ \large Based on Domain Model and Optimization Logic}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{1. Sets (Entities)}
\item $\mathcal{P}$: Set of Projects, where each $p \in \mathcal{P}$ has attributes: id, name, project\_start, project\_end, description, budget, status, target\_audience, priority.
    \item $\mathcal{T}$: Set of Teams, where each $t \in \mathcal{T}$ has attributes: id, name, team\_size, team\_start, team\_status, location, team\_type.
    \item $\mathcal{W}$: Set of Workers, where each $w \in \mathcal{W}$ has attributes: id, name, first\_name, email, start\_date, status, availability.
    \item $\mathcal{F}$: Set of Features, where each $f \in \mathcal{F}$ has attributes: id, title, description, status, priority, estimated\_effort.
    \item $\mathcal{S}$: Set of Skills, where each $s \in \mathcal{S}$ has attributes: id, label, description, level, certified, category.
    \item $\mathcal{R}$: Set of Roles, where each $r \in \mathcal{R}$ has attributes: id, role\_name, description, area\_of\_responsibility.
    \item $\mathcal{PO}$: Set of Product Owners, where each $po \in \mathcal{PO}$ has attributes: id, name, email, availability.
    \item $\mathcal{SM}$: Set of Scrum Masters, where each $sm \in \mathcal{SM}$ has attributes: id, name, email, experience.
    \item $\mathcal{PB}$: Set of Product Backlogs, where each $pb \in \mathcal{PB}$ has attributes: id, created\_on, last\_updated, number\_of\_entries, status.
    \item $\mathcal{SP}$: Set of Sprints, where each $sp \in \mathcal{SP}$ has attributes: id, sprint\_number, start\_date, end\_date, status, achievement\_of\_goal.
    \item $\mathcal{SPP}$: Set of Sprint Plannings, where each $spp \in \mathcal{SPP}$ has attributes: id, date, duration\_(min), moderation, outcome\_documentation.
    \item $\mathcal{DS}$: Set of Daily Scrums, where each $ds \in \mathcal{DS}$ has attributes: id, date, time, duration, moderation.
    \item $\mathcal{SR}$: Set of Sprint Reviews, where each $sr \in \mathcal{SR}$ has attributes: id, date, duration, feedback\_documentation, attendees\_count.
    \item $\mathcal{SRE}$: Set of Sprint Retrospectives, where each $sre \in \mathcal{SRE}$ has attributes: id, date, duration, improvement\_actions, team\_satisfaction, moderation.
    \item $\mathcal{SBL}$: Set of Sprint Backlogs, where each $sbl \in \mathcal{SBL}$ has attributes: id, number\_of\_tasks, last\_updated, status, total\_effort.
    \item $\mathcal{SG}$: Set of Sprint Goals, where each $sg \in \mathcal{SG}$ has attributes: id, objective\_description, achievement\_status, benefit.
    \item $\mathcal{E}$: Set of Epics, where each $e \in \mathcal{E}$ has attributes: id, title, description, priority, status, estimated\_effort.
    \item $\mathcal{US}$: Set of User Stories, where each $us \in \mathcal{US}$ has attributes: id, title, description, acceptance\_criteria, priority, story\_points, status.
    \item $\mathcal{TSK}$: Set of Tasks, where each $tsk \in \mathcal{TSK}$ has attributes: id, title, description, status, effort, type.
    \item $\mathcal{DEV}$: Set of Development Snapshots, where each $dev \in \mathcal{DEV}$ has attributes: id, version\_number, creation\_date, test\_status, deployment\_target, documentation.
    \item $\mathcal{BL}$: Set of Blockers, where each $bl \in \mathcal{BL}$ has attributes: id, title, description, severity, status, detected\_on, resolved\_on.
    \item $\mathcal{SH}$: Set of Stakeholders, where each $sh \in \mathcal{SH}$ has attributes: id, name, organization, role, email, area\_of\_interest, influence\_level, relevance\_to\_feature.
    \item $\mathcal{VEL}$: Set of Velocity Records, where each $vel \in \mathcal{VEL}$ has attributes: id, number\_of\_sprints\_used, avg.\_story\_points, max\_velocity, min\_velocity, trend.
    \item $\mathcal{REP}$: Set of Release Plans, where each $rep \in \mathcal{REP}$ has attributes: id, version, planned\_date, included\_features, status.
    \item $\mathcal{RM}$: Set of Roadmaps, where each $rm \in \mathcal{RM}$ has attributes: id, start\_date, end\_date, milestones, objectives, versions.
    \item $\mathcal{SCB}$: Set of Scrum Boards, where each $scb \in \mathcal{SCB}$ has attributes: id, board\_type, columns\_(todo/done...), number\_of\_cards, last\_updated.
    \item $\mathcal{FED}$: Set of Feature Documentations, where each $fed \in \mathcal{FED}$ has attributes: id, title, description, creation\_date, change\_log, linked\_requirements, author.

\section{2. Indices}
\item $p \in \mathcal{P}$: Index for Projects.
    \item $t \in \mathcal{T}$: Index for Teams.
    \item $w \in \mathcal{W}$: Index for Workers.
    \item $f \in \mathcal{F}$: Index for Features.
    \item $s \in \mathcal{S}$: Index for Skills.
    \item $r \in \mathcal{R}$: Index for Roles.
    \item $sp \in \mathcal{SP}$: Index for Sprints.
    \item $us \in \mathcal{US}$: Index for User Stories.
    \item $tsk \in \mathcal{TSK}$: Index for Tasks.
    \item $bl \in \mathcal{BL}$: Index for Blockers.
    \item $sh \in \mathcal{SH}$: Index for Stakeholders.
    \item $vel \in \mathcal{VEL}$: Index for Velocity records.
    \item $rep \in \mathcal{REP}$: Index for Release Plans.
    \item $rm \in \mathcal{RM}$: Index for Roadmaps.

\section{3. Goals}
Each goal is expressed as an optimization objective with a type (max/min), aggregation (sum or individual), and weight.

\item[\textbf{G0}] \texttt{maximize\_project\_budget}: Maximize total budget across all active projects.
    \[
    \max \sum_{p \in \mathcal{P}} \omega_{G0} \cdot \text{budget}_p \quad \text{where } \omega_{G0} = 1.5
    \]

    \item[\textbf{G1}] \texttt{maximize\_team\_size}: Maximize total team size across all teams.
    \[
    \max \sum_{t \in \mathcal{T}} \omega_{G1} \cdot \text{team\_size}_t \quad \text{where } \omega_{G1} = 1.0
    \]

    \item[\textbf{G2}] \texttt{maximize\_worker\_availability}: Maximize sum of worker availability percentages.
    \[
    \max \sum_{w \in \mathcal{W}} \omega_{G2} \cdot \text{availability}_w \quad \text{where } \omega_{G2} = 1.2
    \]

    \item[\textbf{G3}] \texttt{minimize\_sprint\_duration}: Minimize total span of sprints.
    \[
    \min \sum_{sp \in \mathcal{SP}} \omega_{G3} \cdot (\text{end\_date}_{sp} - \text{start\_date}_{sp}) \quad \text{where } \omega_{G3} = 0.8
    \]

    \item[\textbf{G4}] \texttt{maximize\_story\_points}: Maximize total story points completed.
    \[
    \max \sum_{us \in \mathcal{US}} \omega_{G4} \cdot \text{story\_points}_{us} \quad \text{where } \omega_{G4} = 1.4
    \]

    \item[\textbf{G5}] \texttt{minimize\_task\_effort}: Minimize total task effort.
    \[
    \min \omega_{G5} \cdot \text{effort}_{tsk} \quad \text{per task, where } \omega_{G5} = 0.9
    \]

    \item[\textbf{G6}] \texttt{maximize\_velocity\_trend}: Maximize average velocity trend.
    \[
    \max \sum_{vel \in \mathcal{VEL}} \omega_{G6} \cdot \text{trend}_{vel} \quad \text{where } \omega_{G6} = 1.3
    \]

    \item[\textbf{G7}] \texttt{maximize\_release\_features}: Maximize number of features in release plans.
    \[
    \max \sum_{rep \in \mathcal{REP}} \omega_{G7} \cdot |\text{included\_features}_{rep}| \quad \text{where } \omega_{G7} = 1.1
    \]

    \item[\textbf{G8}] \texttt{minimize\_epic\_estimated\_effort}: Minimize total effort for epics.
    \[
    \min \sum_{e \in \mathcal{E}} \omega_{G8} \cdot \text{estimated\_effort}_e \quad \text{where } \omega_{G8} = 1.0
    \]

    \item[\textbf{G9}] \texttt{maximize\_sprint\_achievement}: Maximize sprint goal achievement.
    \[
    \max \sum_{sp \in \mathcal{SP}} \omega_{G9} \cdot \text{achievement\_of\_goal}_{sp} \quad \text{where } \omega_{G9} = 1.6
    \]

    \item[\textbf{G10}] \texttt{minimize\_blocker\_severity}: Minimize cumulative blocker severity.
    \[
    \min \sum_{bl \in \mathcal{BL}} \omega_{G10} \cdot \text{severity}_{bl} \quad \text{where } \omega_{G10} = 0.7
    \]

    \item[\textbf{G11}] \texttt{maximize\_documentation\_coverage}: Maximize number of documented features.
    \[
    \max \sum_{fed \in \mathcal{FED}} \omega_{G11} \cdot \mathbb{I}(\text{linked\_requirements}_{fed} \neq \emptyset) \quad \text{where } \omega_{G11} = 1.0
    \]

    \item[\textbf{G12}] \texttt{minimize\_worker\_start\_date}: Favor earlier worker onboarding.
    \[
    \min \sum_{w \in \mathcal{W}} \omega_{G12} \cdot \text{start\_date}_w \quad \text{where } \omega_{G12} = 0.8
    \]

    \item[\textbf{G13}] \texttt{maximize\_satisfaction\_score}: Maximize team satisfaction in retrospectives.
    \[
    \max \sum_{sre \in \mathcal{SRE}} \omega_{G13} \cdot \text{team\_satisfaction}_{sre} \quad \text{where } \omega_{G13} = 1.5
    \]

    \item[\textbf{G14}] \texttt{maximize\_planned\_releases}: Maximize number of versions in roadmap.
    \[
    \max \sum_{rm \in \mathcal{RM}} \omega_{G14} \cdot |\text{versions}_{rm}| \quad \text{where } \omega_{G14} = 1.1
    \]

\section{4. Conditions}
Each condition represents a constraint that must be satisfied (hard or soft based on weight and criteria type).

\item[\textbf{C0}] \texttt{require\_project\_status}: Project must be active or planned.
    \[
    \text{status}_p \in \{\texttt{active}, \texttt{planned}\}, \quad \forall p \in \mathcal{P}, \quad \omega_{C0} = 2.0
    \]

    \item[\textbf{C1}] \texttt{require\_team\_status}: Team must be active.
    \[
    \text{team\_status}_t = \texttt{active}, \quad \forall t \in \mathcal{T}, \quad \omega_{C1} = 1.8
    \]

    \item[\textbf{C2}] \texttt{require\_worker\_status}: Worker must be active.
    \[
    \text{status}_w = \texttt{active}, \quad \forall w \in \mathcal{W}, \quad \omega_{C2} = 2.2
    \]

    \item[\textbf{C3}] \texttt{require\_task\_status}: Only tasks with status 'To Do' or 'In Progress' are schedulable.
    \[
    \text{status}_{tsk} \in \{\texttt{To Do}, \texttt{In Progress}\}, \quad \forall tsk \in \mathcal{TSK}, \quad \omega_{C3} = 1.5
    \]

    \item[\textbf{C4}] \texttt{require\_sprint\_status}: Sprint must be upcoming or active.
    \[
    \text{status}_{sp} \in \{\texttt{upcoming}, \texttt{active}\}, \quad \forall sp \in \mathcal{SP}, \quad \omega_{C4} = 2.0
    \]

    \item[\textbf{C5}] \texttt{require\_skill\_certification}: Only certified skills are valid for assignment.
    \[
    \text{certified}_s = \texttt{true}, \quad \forall s \in \mathcal{S}, \quad \omega_{C5} = 1.7
    \]

    \item[\textbf{C6}] \texttt{require\_role\_area}: Role must match required area of responsibility.
    \[
    \text{area\_of\_responsibility}_r \in \mathcal{A}_{\text{required}}, \quad \forall r \in \mathcal{R}, \quad \omega_{C6} = 1.6
    \]

    \item[\textbf{C7}] \texttt{require\_feature\_priority}: Feature priority must be high or medium.
    \[
    \text{priority}_f \in \{\texttt{high}, \texttt{medium}\}, \quad \forall f \in \mathcal{F}, \quad \omega_{C7} = 1.4
    \]

    \item[\textbf{C8}] \texttt{require\_user\_story\_status}: Only open or in-progress stories are selectable.
    \[
    \text{status}_{us} \in \{\texttt{open}, \texttt{in progress}\}, \quad \forall us \in \mathcal{US}, \quad \omega_{C8} = 1.9
    \]

    \item[\textbf{C9}] \texttt{require\_blocker\_status}: Only unresolved blockers are tracked.
    \[
    \text{status}_{bl} = \texttt{open}, \quad \forall bl \in \mathcal{BL}, \quad \omega_{C9} = 1.3
    \]

    \item[\textbf{C10}] \texttt{require\_velocity\_min}: Velocity must exceed minimum threshold.
    \[
    \text{min\_velocity}_{vel} \leq \text{avg.\_story\_points}_{vel}, \quad \forall vel \in \mathcal{VEL}, \quad \omega_{C10} = 1.8
    \]

    \item[\textbf{C11}] \texttt{require\_release\_status}: Only planned or active releases are valid.
    \[
    \text{status}_{rep} \in \{\texttt{planned}, \texttt{active}\}, \quad \forall rep \in \mathcal{REP}, \quad \omega_{C11} = 1.5
    \]

    \item[\textbf{C12}] \texttt{require\_board\_type}: Scrum board must be digital or physical.
    \[
    \text{board\_type}_{scb} \in \{\texttt{digital}, \texttt{physical}\}, \quad \forall scb \in \mathcal{SCB}, \quad \omega_{C12} = 1.2
    \]

    \item[\textbf{C13}] \texttt{require\_snapshot\_test\_status}: Snapshot must have passed tests to be deployable.
    \[
    \text{test\_status}_{dev} = \texttt{passed}, \quad \forall dev \in \mathcal{DEV}, \quad \omega_{C13} = 2.1
    \]

    \item[\textbf{C14}] \texttt{require\_stakeholder\_relevance}: Stakeholder relevance must be medium or high.
    \[
    \text{relevance\_to\_feature}_{sh} \in \{\texttt{medium}, \texttt{high}\}, \quad \forall sh \in \mathcal{SH}, \quad \omega_{C14} = 1.6
    \]

\section{5. DecisionVariables}
These are the variables that the optimization model can adjust.

\item[\textbf{DV0}] $\mathbf{x}_{t,p} \in \{0,1\}$: Assignment of team $t$ to project $p$. 1 if assigned, 0 otherwise.
    \item[\textbf{DV1}] $\mathbf{y}_{w,t} \in \{0,1\}$: Assignment of worker $w$ to team $t$.
    \item[\textbf{DV2}] $\mathbf{z}_{w,s} \in \{0,1\}$: Worker $w$ possesses skill $s$ and is certified.
    \item[\textbf{DV3}] $\mathbf{r}_{w,r} \in \{0,1\}$: Worker $w$ takes on role $r$ in a team.
    \item[\textbf{DV4}] $\mathbf{b}_{f,pb} \in \{0,1\}$: Feature $f$ is selected in product backlog $pb$.
    \item[\textbf{DV5}] $\mathbf{g}_{sp} \in \{1,2,3,4,5\}$: Sprint goal $sp$ is rated by objective strength (1–5).
    \item[\textbf{DV6}] $\mathbf{d}_{sp} \in \mathbb{Z}^+$: Duration of sprint $sp$ in days, $1 \leq d_{sp} \leq 30$.
    \item[\textbf{DV7}] $\mathbf{e}_{tsk} \in \mathbb{Z}^+$: Estimated effort for task $tsk$, $1 \leq e_{tsk} \leq 40$.
    \item[\textbf{DV8}] $\mathbf{s}_{us} \in \{1,2,3,5,8,13\}$: Story points assigned to user story $us$.
    \item[\textbf{DV9}] $\mathbf{h}_{bl} \in \mathbb{Z}^+$: Estimated resolution time (days) for blocker $bl$, $0 \leq h_{bl} \leq 60$.
    \item[\textbf{DV10}] $\mathbf{v}_{rep} \in \mathbb{R}^+$: Release version number, $1.0 \leq v_{rep} \leq 10.0$.
    \item[\textbf{DV11}] $\mathbf{u}_{fed} \in \mathbb{Z}^+$: Number of documentation updates per sprint for $fed$, $0 \leq u_{fed} \leq 5$.
    \item[\textbf{DV12}] $\mathbf{sat}_{sre} \in \{1,2,3,4,5\}$: Target team satisfaction level for retrospective $sre$.
    \item[\textbf{DV13}] $\mathbf{vel}_{pred} \in \mathbb{Z}^+$: Predicted velocity for next sprint, $5 \leq vel_{pred} \leq 50$.
    \item[\textbf{DV14}] $\mathbf{dep}_{dev} \in \{0,1,2\}$: Deployment target: 0=dev, 1=staging, 2=production.

\end{document}