\documentclass{article}
\usepackage{amsmath}

\title{Optimization Model for Software Development Company Using Scrum}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Mathematical Representation of the Optimization Problem}

% Decision Variables
\subsection*{Decision Variables}
Let \( x_i \) represent decision variables where:
- Numeric variables are continuous or discrete with specified domains.
- Boolean variables are represented by binary values (0 or 1).

% Objective Function
\subsection*{Objective Function}
The objective function aims to maximize or minimize certain criteria based on goals:

\[
\text{Maximize/Minimize } Z = \sum_{i} w_i f_i(x)
\]

Where:
\begin{itemize}
    \item \( w_i \): Weight assigned to the goal \( i \).
    \item \( f_i(x) \): Function representing how well decision variables satisfy goal \( i \).
\end{itemize}

% Constraints
\subsection*{Constraints}

1. Budget Constraint (Maximize Project Efficiency):
   \[
   \sum_{j} x_1[j] \leq \text{Total Budget}
   \]

2. Team Size Optimization (Optimize Team Size):
   \[
   \min(\text{Var}(x_2)) \quad \text{subject to } 3 \leq x_2 \leq 12
   \]

3. Skill Matching (Enhance Skill Matching):
   \[
   \sum_{k} x_3[k] \geq \text{Minimum Skill Match Threshold}
   \]

4. Role Clarity (Ensure Role Clarity):
   \[
   x_4 \geq \text{Clarity Threshold}
   \]

5. Bug Severity Prioritization (Prioritize Critical Bugs):
   \[
   \sum_{m} x_5[m] \cdot \text{Severity}[m] \leq \text{Max Allowable Risk Level}
   \]

6. Backlog Relevance (Streamline Product Backlog):
   \[
   \sum_{n} x_6[n] \geq \text{Relevance Threshold}
   \]

7. Sprint Goal Achievement (Achieve Sprint Goals):
   \[
   x_7 \geq \text{Goal Achievement Threshold}
   \]

8. Feature Priority (Focus on High-Priority Features):
   \[
   \sum_{o} x_8[o] \cdot \text{Priority}[o] \leq \text{Max Feature Load}
   \]

9. Task Distribution Equality (Even Task Distribution):
   \[
   \max(\text{Var}(x_9)) \quad \text{should be minimized}
   \]

10. Stakeholder Involvement (Maximize Stakeholder Involvement):
    \[
    x_{10} \geq \text{Involvement Threshold}
    \]

11. Scrum Process Improvement (Continuous Scrum Enhancement):
    \[
    x_{11} \leq \text{Improvement Ceiling}
    \]

12. Variance in Velocity (Reduce Velocity Variance):
    \[
    \min(\text{Var}(x_{12}))
    \]

13. Roadmap Alignment (Ensure Feature Roadmapping):
    \[
    x_{13} \geq \text{Alignment Threshold}
    \]

14. Documentation Completeness (Maintain Complete Documentation):
    \[
    x_{14} = 1
    \]

15. Team Autonomy (Foster Team Independence):
    \[
    x_{15} \geq \text{Autonomy Threshold}
    \]

16. Release Schedule Adherence (Optimize Release Schedules):
    \[
    x_{16} \geq \text{Adherence Threshold}
    \]

17. User Story Clarity (Define Clear Acceptance Criteria):
    \[
    x_{17} = 1
    \]

18. Skill Development Opportunities (Encourage Continuous Learning):
    \[
    \sum_{p} x_{18}[p] \geq \text{Opportunity Threshold}
    \]

19. Epic Decomposition Efficiency (Break Down Epics Effectively):
    \[
    x_{19} \geq \text{Efficiency Threshold}
    \]

20. Meeting Reduction Potential (Reduce Unnecessary Meetings):
    \[
    x_{20} = 1
    \]

21. Talent Retention Rate (Encourage Employee Satisfaction):
    \[
    x_{21} \geq \text{Retention Threshold}
    \]

22. Stakeholder Update Frequency (Ensure Clear Stakeholder Updates):
    \[
    x_{22} \geq \text{Update Frequency Threshold}
    \]

23. Backlog Refinement Efficiency (Regular Backlog Refinement):
    \[
    x_{23} \geq \text{Efficiency Threshold}
    \]

24. Risk Mitigation Effectiveness (Identify and Mitigate Risks):
    \[
    x_{24} \geq \text{Effectiveness Threshold}
    \]

25. Versatile Team Capability (Maintain Versatile Teams):
    \[
    x_{25} \geq \text{Capability Threshold}
    \]

\end{document}