\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

\title{Software Development Optimization Model}
\date{}
\maketitle

\section{Introduction}

This document presents a mathematical model for optimizing software development processes, incorporating elements from Scrum and focusing on maximizing value delivery while respecting constraints.

\section{Sets}

\begin{itemize}
    \item $E$: Set of Employees
    \item $S$: Set of Skills
    \item $F$: Set of Features
    \item $U$: Set of User Stories
    \item $T$: Set of Tasks
    \item $Sp$: Set of Sprints
\end{itemize}

\section{Parameters}

\begin{itemize}
    \item $c_f$: Cost of a Feature
    \item $v_e$: Velocity of a team
    \item $w_fp$: Priority weight for Features
    \item $a_s$: Skill availability
    \item $est_u$: Estimated effort for User Stories (Story Points)
    \item $cap_s$: Sprint Capacity
    \item $req_u$: Requirement linkage (Boolean, 1 if User Story linked to Feature and Project)
\end{itemize}

\section{Decision Variables}

\begin{itemize}
    \item $x_{et}$: Binary variable. 1 if Employee $e$ is assigned to Task $t$, 0 otherwise.
    \item $y_{us}$: Binary variable. 1 if User Story $u$ is selected for a Sprint, 0 otherwise.
    \item $z_{es}$:  Numeric variable. Effort level assigned to Employee $e$ to utilize Skill $s$.
    \item $p_{us}$: Numeric variable. Adjustment factor applied to User Story $u$'s effort estimate.
\end{itemize}

\section{Objective Function}

Maximize Total Value delivered (based on Feature priority and User Story effort)

\begin{equation}
\text{Maximize } \sum_{f \in F} w_{fp} \sum_{u \in U} y_{us} (est_{u} + p_{us})
\end{equation}

\section{Constraints}

\subsection{Resource Constraints}

\begin{enumerate}
    \item Each Task can be assigned to only one Employee.
    \begin{equation}
    \sum_{e \in E} x_{et} = 1 \quad \forall t \in T
    \end{equation}
    \item Employee capacity constraint.
    \begin{equation}
    \sum_{t \in T} x_{et} \leq 1 \quad \forall e \in E
    \end{equation}
    \item Skill utilization constraint.
    \begin{equation}
    \sum_{s \in S} z_{es} \leq 1 \quad \forall e \in E
    \end{equation}
\end{enumerate}

\subsection{Sprint Planning Constraints}

\begin{enumerate}
    \item Sprint capacity limit.
    \begin{equation}
    \sum_{u \in U} y_{us} (est_{u} + p_{us}) \leq cap_{s} \quad \forall Sp \in Sp
    \end{equation}
\end{enumerate}

\subsection{Requirement Traceability}

\begin{equation}
y_{us} = req_{u} \quad \forall u \in U
\end{equation}

\subsection{Employee Capacity}

\begin{equation}
\sum_{t \in T} x_{et} +  \sum_{u \in U} x_{et} \leq 1 \quad \forall e \in E
\end{equation}

\section{Variable Bounds}

\begin{itemize}
    \item $x_{et} \in \{0, 1\}$
    \item $y_{us} \in \{0, 1\}$
    \item $z_{es} \geq 0$
    \item $p_{us} \geq 0$
\end{itemize}

\end{document}