\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{tocloft}
\usepackage{enumitem}

\geometry{margin=1in}
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}
\titleformat{\subsection}{\bfseries}{}{0em}{}

\title{\Huge Optimization Model for Scrum-Based Software Development\\[0.5cm]
\Large Integrating Entities, Goals, Conditions, and Decision Variables}
\author{\Large AI Assistant \\ Software Development Optimization Team}
\date{\today}

\begin{document}

\maketitle

\tableofcontents
\newpage

\section{1. Sets (Entities)}

The following sets represent core entities in the Scrum-based software development domain.

\item $ \mathcal{P} $: Set of Projects, with attributes: id, name, project\_start, project\_end, description, budget, status, target\_audience, priority.
    \item $ \mathcal{T} $: Set of Teams, with attributes: id, name, team\_size, team\_start, team\_status, location, team\_type.
    \item $ \mathcal{W} $: Set of Workers, with attributes: id, name, first\_name, email, start\_date, status, availability.
    \item $ \mathcal{F} $: Set of Features, with attributes: id, title, description, status, priority, estimated\_effort.
    \item $ \mathcal{S} $: Set of Skills, with attributes: id, label, description, level, certified, category.
    \item $ \mathcal{R} $: Set of Roles, with attributes: id, role\_name, description, area\_of\_responsibility.
    \item $ \mathcal{PO} $: Set of Product Owners, with attributes: id, name, email, availability.
    \item $ \mathcal{SM} $: Set of Scrum Masters, with attributes: id, name, email, experience.
    \item $ \mathcal{PB} $: Set of Product Backlogs, with attributes: id, created\_on, last\_updated, number\_of\_entries, status.
    \item $ \mathcal{SP} $: Set of Sprints, with attributes: id, sprint\_number, start\_date, end\_date, status, achievement\_of\_goal.
    \item $ \mathcal{SPP} $: Set of Sprint Plannings, with attributes: id, date, duration\_(min), moderation, outcome\_documentation.
    \item $ \mathcal{DS} $: Set of Daily Scrums, with attributes: id, date, time, duration, moderation.
    \item $ \mathcal{SR} $: Set of Sprint Reviews, with attributes: id, date, duration, feedback\_documentation, attendees\_count.
    \item $ \mathcal{SRE} $: Set of Sprint Retrospectives, with attributes: id, date, duration, improvement\_actions, team\_satisfaction, moderation.
    \item $ \mathcal{SBL} $: Set of Sprint Backlogs, with attributes: id, number\_of\_tasks, last\_updated, status, total\_effort.
    \item $ \mathcal{SG} $: Set of Sprint Goals, with attributes: id, objective\_description, achievement\_status, benefit.
    \item $ \mathcal{E} $: Set of Epics, with attributes: id, title, description, priority, status, estimated\_effort.
    \item $ \mathcal{US} $: Set of User Stories, with attributes: id, title, description, acceptance\_criteria, priority, story\_points, status.
    \item $ \mathcal{TSK} $: Set of Tasks, with attributes: id, title, description, status, effort, type.
    \item $ \mathcal{DEV} $: Set of Development Snapshots, with attributes: id, version\_number, creation\_date, test\_status, deployment\_target, documentation.
    \item $ \mathcal{BL} $: Set of Blockers, with attributes: id, title, description, severity, status, detected\_on, resolved\_on.
    \item $ \mathcal{SH} $: Set of Stakeholders, with attributes: id, name, organization, role, email, area\_of\_interest, influence\_level, relevance\_to\_feature.
    \item $ \mathcal{VEL} $: Set of Velocity records, with attributes: id, number\_of\_sprints\_used, avg.\_story\_points, max\_velocity, min\_velocity, trend.
    \item $ \mathcal{REP} $: Set of Release Plans, with attributes: id, version, planned\_date, included\_features, status.
    \item $ \mathcal{RM} $: Set of Roadmaps, with attributes: id, start\_date, end\_date, milestones, objectives, versions.
    \item $ \mathcal{SCB} $: Set of Scrum Boards, with attributes: id, board\_type, columns\_(todo/done...), number\_of\_cards, last\_updated.
    \item $ \mathcal{FED} $: Set of Feature Documentations, with attributes: id, title, description, creation\_date, change\_log, linked\_requirements, author.

\section{2. Indices}

Indices are used to reference elements within the defined sets.

\item $ p \in \mathcal{P} $: Index for Projects.
    \item $ t \in \mathcal{T} $: Index for Teams.
    \item $ w \in \mathcal{W} $: Index for Workers.
    \item $ f \in \mathcal{F} $: Index for Features.
    \item $ s \in \mathcal{S} $: Index for Skills.
    \item $ r \in \mathcal{R} $: Index for Roles.
    \item $ po \in \mathcal{PO} $: Index for Product Owners.
    \item $ sm \in \mathcal{SM} $: Index for Scrum Masters.
    \item $ sp \in \mathcal{SP} $: Index for Sprints.
    \item $ us \in \mathcal{US} $: Index for User Stories.
    \item $ tk \in \mathcal{TSK} $: Index for Tasks.
    \item $ bl \in \mathcal{BL} $: Index for Blockers.
    \item $ sh \in \mathcal{SH} $: Index for Stakeholders.
    \item $ v \in \mathcal{VEL} $: Index for Velocity records.
    \item $ rep \in \mathcal{REP} $: Index for Release Plans.
    \item $ rm \in \mathcal{RM} $: Index for Roadmaps.

\section{3. Goals}

Optimization goals aim to maximize or minimize key performance indicators. Each goal is defined with logical intent and mathematical expression.

\item \textbf{G0: maximize\_project\_budget} \\
    Maximize total budget across selected projects. \\
    $ \max \sum_{p \in \mathcal{P}} x_p \cdot \text{budget}_p $, where $ x_p \in \{0,1\} $ indicates project selection.

    \item \textbf{G1: maximize\_team\_size} \\
    Maximize the total team size across assigned teams. \\
    $ \max \sum_{t \in \mathcal{T}} y_t \cdot \text{team\_size}_t $, where $ y_t \in \{0,1\} $ indicates team assignment.

    \item \textbf{G2: maximize\_worker\_availability} \\
    Maximize total worker availability. \\
    $ \max \sum_{w \in \mathcal{W}} z_w \cdot \text{availability}_w $, where $ z_w \in \{0,1\} $ if worker is active.

    \item \textbf{G3: minimize\_feature\_estimated\_effort} \\
    Minimize effort required for all features. \\
    $ \min \sum_{f \in \mathcal{F}} \text{estimated\_effort}_f $

    \item \textbf{G4: maximize\_sprint\_achievement\_of\_goal} \\
    Maximize average sprint goal achievement. \\
    $ \max \frac{1}{|\mathcal{SP}|} \sum_{sp \in \mathcal{SP}} \text{achievement\_of\_goal}_{sp} $

    \item \textbf{G5: maximize\_sprint\_velocity} \\
    Maximize average velocity of teams. \\
    $ \max \sum_{v \in \mathcal{VEL}} \text{avg.\_story\_points}_v $

    \item \textbf{G6: minimize\_sprint\_duration} \\
    Minimize total sprint duration. \\
    $ \min \sum_{sp \in \mathcal{SP}} (\text{end\_date}_{sp} - \text{start\_date}_{sp}) $

    \item \textbf{G7: maximize\_user\_story\_story\_points} \\
    Maximize completed story points. \\
    $ \max \sum_{us \in \mathcal{US}} \delta_{us} \cdot \text{story\_points}_{us} $, where $ \delta_{us} = 1 $ if story is completed.

    \item \textbf{G8: minimize\_blocker\_severity} \\
    Minimize average blocker severity. \\
    $ \min \frac{1}{|\mathcal{BL}|} \sum_{bl \in \mathcal{BL}} \text{severity}_{bl} \cdot \mathbb{I}(\text{status}_{bl} = \text{open}) $

    \item \textbf{G9: maximize\_release\_plan\_included\_features} \\
    Maximize number of features in release plans. \\
    $ \max \sum_{rep \in \mathcal{REP}} |\text{included\_features}_{rep}| $

    \item \textbf{G10: maximize\_documentation\_change\_log} \\
    Maximize documentation update frequency. \\
    $ \max \sum_{fed \in \mathcal{FED}} |\text{change\_log}_{fed}| $

    \item \textbf{G11: minimize\_worker\_start\_date} \\
    Favor earlier-hired (more experienced) workers. \\
    $ \min \sum_{w \in \mathcal{W}} z_w \cdot \text{start\_date}_w $

    \item \textbf{G12: maximize\_sprint\_retrospective\_team\_satisfaction} \\
    Maximize team morale from retrospectives. \\
    $ \max \sum_{sre \in \mathcal{SRE}} \text{team\_satisfaction}_{sre} $

    \item \textbf{G13: minimize\_task\_effort} \\
    Minimize total task effort in sprints. \\
    $ \min \sum_{tk \in \mathcal{TSK}} \text{effort}_{tk} $

    \item \textbf{G14: maximize\_roadmap\_milestones} \\
    Maximize number of achieved milestones. \\
    $ \max \sum_{rm \in \mathcal{RM}} |\text{milestones}_{rm}| $

\section{4. Conditions}

Constraints enforce mandatory or conditional rules based on entity states.

\item \textbf{C0: require\_project\_status\_active} \\
    Only active projects are eligible. \\
    $ x_p = 1 \Rightarrow \text{status}_p = \text{active}, \quad \forall p \in \mathcal{P} $

    \item \textbf{C1: require\_team\_status\_active} \\
    Only active teams can be assigned. \\
    $ y_t = 1 \Rightarrow \text{team\_status}_t = \text{active}, \quad \forall t \in \mathcal{T} $

    \item \textbf{C2: require\_worker\_status\_active} \\
    Only active workers may be assigned. \\
    $ z_w = 1 \Rightarrow \text{status}_w = \text{active}, \quad \forall w \in \mathcal{W} $

    \item \textbf{C3: require\_feature\_status\_not\_done} \\
    Exclude completed features. \\
    $ \text{status}_f \neq \text{done}, \quad \forall f \in \mathcal{F} $

    \item \textbf{C4: require\_user\_story\_status\_todo} \\
    Only user stories not started are assignable. \\
    $ \delta_{us} = 1 \Rightarrow \text{status}_{us} = \text{todo}, \quad \forall us \in \mathcal{US} $

    \item \textbf{C5: require\_task\_status\_blocked} \\
    Identify blocked tasks. \\
    $ \gamma_{tk} = 1 \text{ if } \text{status}_{tk} = \text{blocked}, \quad \forall tk \in \mathcal{TSK} $

    \item \textbf{C6: require\_blocker\_status\_open} \\
    Only open blockers are considered. \\
    $ \text{status}_{bl} = \text{open}, \quad \forall bl \in \mathcal{BL} $

    \item \textbf{C7: require\_sprint\_status\_active} \\
    Only active sprints are valid. \\
    $ \text{status}_{sp} = \text{active}, \quad \forall sp \in \mathcal{SP} $

    \item \textbf{C8: require\_role\_certified} \\
    Assigned roles must be formally defined. \\
    $ r \in \mathcal{R} \Rightarrow \text{area\_of\_responsibility}_r \neq \emptyset $

    \item \textbf{C9: require\_skill\_certified} \\
    Only certified skills are valid. \\
    $ s \in \mathcal{S} \Rightarrow \text{certified}_s = \text{true} $

    \item \textbf{C10: require\_velocity\_trend\_positive} \\
    Only teams with positive trend are selected. \\
    $ \text{trend}_v > 0, \quad \forall v \in \mathcal{VEL} $

    \item \textbf{C11: require\_release\_status\_planned} \\
    Only planned releases are included. \\
    $ \text{status}_{rep} = \text{planned}, \quad \forall rep \in \mathcal{REP} $

    \item \textbf{C12: require\_scumb\_board\_active} \\
    Scrum Board must be active. \\
    $ \text{board\_type}_{scb} \in \{\text{active}, \text{digital}\}, \quad \forall scb \in \mathcal{SCB} $

    \item \textbf{C13: require\_epic\_status\_open} \\
    Only open epics are eligible. \\
    $ \text{status}_e = \text{open}, \quad \forall e \in \mathcal{E} $

    \item \textbf{C14: require\_stakeholder\_relevance\_high} \\
    Only high-relevance stakeholders are considered. \\
    $ \text{relevance\_to\_feature}_{sh} \geq 4, \quad \forall sh \in \mathcal{SH} $

\section{5. DecisionVariables}

These are the variables optimized in the model.

\item $ x_p \in \{0,1\} $: Project $ p $ is selected.
    \item $ y_t \in \{0,1\} $: Team $ t $ is assigned to a project.
    \item $ z_w \in \{0,1\} $: Worker $ w $ is assigned to a task.
    \item $ slevel_{w,s} \in [1,5] $: Skill level of worker $ w $ in skill $ s $.
    \item $ e_{tk} \in [0,100] $: Effort assigned to task $ tk $.
    \item $ d_{sp} \in [5,30] $: Duration of sprint $ sp $ in days.
    \item $ prio_{us} \in \{1,2,3,4,5\} $: Priority of user story $ us $.
    \item $ spoints_{us} \in \{1,2,3,5,8,13\} $: Story points assigned to user story $ us $.
    \item $ sev_{bl} \in \{1,2,3,4,5\} $: Severity level of blocker $ bl $.
    \item $ n_{v} \in \{3,4,\dots,10\} $: Number of sprints used in velocity calculation.
    \item $ v_{rep} \in [1.0, 10.0] $: Version number of release plan $ rep $.
    \item $ w_{rm} \in [0.1, 5.0] $: Weight of objective in roadmap $ rm $.
    \item $ u_{fed} \in \mathbb{Z}^+ \cup \{0\} $: Number of updates to feature documentation $ fed $.
    \item $ a_{sre} \in \{0,1,\dots,20\} $: Number of improvement actions from retrospective $ sre $.
    \item $ c_{scb} \in \{3,4,5,6,7\} $: Number of columns on Scrum Board $ scb $.

\end{document}