\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{amsmath}
\usepackage{hyperref}

\title{Optimization Model for Scrum Software Development}
\author{AI Assistant}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}

This document outlines an optimization model for software development using the Scrum framework. The model aims to maximize value delivery while considering various constraints and priorities.  The model utilizes a set of goals, conditions, and decision variables to achieve optimal resource allocation and project execution.

\section{Sets (Entities)}

The following sets represent the entities involved in the optimization model:

\begin{itemize}
    \item \textbf{Projects}: Represents the software projects being developed.
    \item \textbf{Teams}: Represents the development teams.
    \item \textbf{Workers}: Represents the individual team members.
    \item \textbf{Features}: Represents the functionalities being implemented.
    \item \textbf{User Stories}: Represents the requirements from the user's perspective.
    \item \textbf{Tasks}: Represents the smallest units of work within a sprint.
\end{itemize}

\section{Indices}

Indices are used to denote the specific elements within each set.  For example, $i$ represents an index for projects, $j$ represents an index for teams, and so on.

\section{Goals}

The optimization model seeks to achieve the following goals:

\begin{itemize}
    \item \textbf{Maximize Team Velocity (G0)}: $\max \sum_{j} \text{team\_size}_j$
    \item \textbf{Minimize Project Cost (G1)}: $\min \sum_{i} \text{budget}_i$
    \item \textbf{Maximize Feature Priority (G2)}: $\max \sum_{f} \text{priority}_f$
\end{itemize}

\section{Conditions}

The optimization model is subject to the following conditions:

\begin{itemize}
    \item \textbf{Feature Priority High (C0)}: $\text{priority}_f \ge 3$
    \item \textbf{Worker Status Active (C1)}: $\text{status}_w = \text{Active}$
\end{itemize}

\section{DecisionVariables}

The following are the decision variables that will be used:

\begin{itemize}
    \item \textbf{Team Size (DV0)}: The number of team members assigned to a project.
    \item \textbf{Budget Allocation (DV1)}: The amount of budget allocated to a project.
\end{itemize}

\end{document}