\documentclass{article}
\usepackage{amsmath, amssymb}
\usepackage{enumitem}
\title{Scrum Optimization Model}
\author{}
\date{}

\begin{document}

\maketitle

\section{Objective Function}
Maximize alignment with Scrum principles and stakeholder needs while balancing workload and minimizing risks:
$$
\text{Maximize} \left( 
\sum_{s \in \text{Sprints}} \alpha \cdot \text{SprintGoalAchieved}(s) 
+ \sum_{t \in \text{Tasks}} \beta \cdot \text{SkillMatch}(e, s) 
+ \sum_{e \in \text{Employees}} \gamma \cdot \text{EmployeeAvailability}(e, s) 
- \sum_{b \in \text{Blockers}} \delta \cdot \text{BlockerResolved}(b) 
\right)
$$
Where:
\begin{itemize}
    \item $\alpha, \beta, \gamma, \delta$: Weights for prioritizing goals.
    \item $\text{SprintGoalAchieved}(s) \in \{0,1\}$: Binary variable indicating whether sprint $s$ achieves its goal.
    \item $\text{SkillMatch}(e, s) \in \{0,1\}$: Binary variable indicating whether employee $e$ has the required skill for task $s$.
    \item $\text{EmployeeAvailability}(e, s) \in \mathbb{Z}^+$: Hours available to employee $e$ in sprint $s$.
    \item $\text{BlockerResolved}(b) \in \{0,1\}$: Binary variable indicating whether blocker $b$ is resolved.
\end{itemize}

---

\section{Decision Variables}
\begin{itemize}
    \item **Binary Variables**:
    \begin{itemize}
        \item $\text{TaskAssignment}(t, e) \in \{0,1\}$: Task $t$ is assigned to employee $e$.
        \item $\text{BlockerResolved}(b) \in \{0,1\}$: Blocker $b$ is resolved.
        \item $\text{SprintGoalAchieved}(s) \in \{0,1\}$: Sprint $s$ achieves its goal.
        \item $\text{SkillMatch}(e, s) \in \{0,1\}$: Employee $e$ has the required skill for task $s$.
    \end{itemize}
    \item **Continuous Variables**:
    \begin{itemize}
        \item $\text{SprintStartDate}(s) \in \mathbb{R}^+$: Start time of sprint $s$.
        \item $\text{EmployeeAvailability}(e, s) \in \mathbb{Z}^+$: Hours available to employee $e$ in sprint $s$.
        \item $\text{TaskEffort}(t) \in \mathbb{Z}^+$: Effort required for task $t$.
        \item $\text{TeamUtilizationRate}(t, s) \in [0,1]$: Percentage of employee capacity used in sprint $s$.
    \end{itemize}
\end{itemize}

---

\section{Constraints}
\subsection{Hard Constraints (Must-Match / Cannot-Match)}
\begin{enumerate}
    \item **Task Assignment**: 
    $$
    \sum_{e \in \text{Employees}} \text{TaskAssignment}(t, e) = 1 \quad \forall t \in \text{Tasks}
    $$
    (Each task is assigned to exactly one employee.) \label{constraint:task-assignment}

    \item **Skill Matching**: 
    $$
    \text{SkillMatch}(e, s) = 1 \quad \text{if } \text{TaskAssignment}(t, e) = 1 \text{ and task } t \text{ requires skill } s
    $$
    (Tasks can only be assigned to employees with the required skills.) \label{constraint:skill-matching}

    \item **No Overlapping Sprints**: 
    $$
    \text{SprintStartDate}(s_i) + \text{Duration}(s_i) \leq \text{SprintStartDate}(s_j) \quad \forall s_i, s_j \in \text{Sprints}, i \neq j
    $$
    (Sprints cannot overlap.) \label{constraint:no-overlap}

    \item **Blocker Resolution**: 
    $$
    \text{BlockerResolved}(b) = 1 \quad \forall b \in \text{Blockers}
    $$
    (All blockers must be resolved.) \label{constraint:blocker-resolution}

    \item **Sprint Goal Achievement**: 
    $$
    \text{SprintGoalAchieved}(s) = 1 \quad \text{if } \sum_{t \in \text{Tasks}(s)} \text{TaskAssignment}(t, e) \cdot \text{TaskEffort}(t) \leq \text{TeamCapacity}(s)
    $$
    (A sprint goal is achieved only if the total task effort is within team capacity.) \label{constraint:sprint-goal}
\end{enumerate}

\subsection{Soft Constraints (Can-Match)}
\begin{enumerate}
    \item **Workload Balance**: 
    $$
    \text{TeamUtilizationRate}(t, s) \in [\text{MinCapacity}, \text{MaxCapacity}]
    $$
    (Team utilization must stay within predefined bounds to avoid over/underwork.) \label{constraint:workload}

    \item **Stakeholder Priority**: 
    $$
    \sum_{f \in \text{Features}} \text{StakeholderPriority}(f) \cdot \text{FeatureInReleasePlan}(f, r) \geq \text{MinPriority}
    $$
    (High-priority features must be included in release plans.) \label{constraint:stakeholder}
\end{enumerate}

---

\section{Logical Relationships}
\begin{itemize}
    \item **Entity Hierarchy**:
    $$
    \text{Task} \in \text{Epic} \subseteq \text{ReleasePlan} \subseteq \text{Roadmap}, \quad \text{Employee} \in \text{Team}
    $$
    \item **Dependencies**:
    \begin{itemize}
        \item $\text{TaskEffort}(t)$ depends on $\text{TaskAssignment}(t, e)$.
        \item $\text{TeamUtilizationRate}(s)$ depends on $\sum_{t \in \text{Tasks}(s)} \text{TaskEffort}(t)$.
    \end{itemize}
\end{itemize}

---

\section{Example Subproblem}
$$
\text{Maximize} \sum_{t \in T} \text{SkillMatch}(e, s) \cdot \text{TaskAssignment}(t, e)
$$
$$
\text{Subject to:}
$$
\begin{align}
\sum_{e} \text{TaskAssignment}(t, e) &= 1 \quad \forall t \in T \label{eq:sub-task-assignment} \\
\sum_{t} \text{TaskEffort}(t) \cdot \text{TaskAssignment}(t, e) &\leq \text{EmployeeCapacity}(e, s) \quad \forall e \in E \label{eq:sub-capacity}
\end{align}

---

\section{Final Notes}
\begin{itemize}
    \item This model is a **Mixed-Integer Linear Program (MILP)**.
    \item Constraints \ref{constraint:task-assignment}--\ref{constraint:sprint-goal} are hard constraints (must be satisfied).
    \item Constraints \ref{constraint:workload}--\ref{constraint:stakeholder} are soft constraints (optimize for balance).
    \item Use solvers like Gurobi, CPLEX, or open-source alternatives (e.g., CBC, SCIP) for computation.
\end{itemize}

\end{document}