\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, graphicx, geometry, hyperref, enumitem}
\geometry{a4paper, margin=1in}

\title{\textbf{Optimization Model for SCRUM-Based Software Development Planning}}
\author{Domain Modeling & Optimization Team}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{1. Sets (Entities)}

\item $\mathcal{P}$: Set of Projects, where each $p \in \mathcal{P}$ has attributes: id, name, project\_start, project\_end, description, budget, status, target\_audience, priority.
    \item $\mathcal{T}$: Set of Teams, where each $t \in \mathcal{T}$ has attributes: id, name, team\_size, team\_start, team\_status, location, team\_type.
    \item $\mathcal{W}$: Set of Workers, where each $w \in \mathcal{W}$ has attributes: id, name, first\_name, email, start\_date, status, availability.
    \item $\mathcal{F}$: Set of Features, where each $f \in \mathcal{F}$ has attributes: id, title, description, status, priority, estimated\_effort.
    \item $\mathcal{S}$: Set of Skills, where each $s \in \mathcal{S}$ has attributes: id, label, description, level, certified, category.
    \item $\mathcal{R}$: Set of Roles, where each $r \in \mathcal{R}$ has attributes: id, role\_name, description, area\_of\_responsibility.
    \item $\mathcal{PO}$: Set of Product Owners, where each $po \in \mathcal{PO}$ has attributes: id, name, email, availability.
    \item $\mathcal{SM}$: Set of Scrum Masters, where each $sm \in \mathcal{SM}$ has attributes: id, name, email, experience.
    \item $\mathcal{PB}$: Set of Product Backlogs, where each $pb \in \mathcal{PB}$ has attributes: id, created\_on, last\_updated, number\_of\_entries, status.
    \item $\mathcal{SP}$: Set of Sprints, where each $sp \in \mathcal{SP}$ has attributes: id, sprint\_number, start\_date, end\_date, status, achievement\_of\_goal.
    \item $\mathcal{SPP}$: Set of Sprint Plannings, where each $spp \in \mathcal{SPP}$ has attributes: id, date, duration\_$(min)$, moderation, outcome\_documentation.
    \item $\mathcal{DS}$: Set of Daily Scrums, where each $ds \in \mathcal{DS}$ has attributes: id, date, time, duration, moderation.
    \item $\mathcal{SR}$: Set of Sprint Reviews, where each $sr \in \mathcal{SR}$ has attributes: id, date, duration, feedback\_documentation, attendees\_count.
    \item $\mathcal{SRE}$: Set of Sprint Retrospectives, where each $sre \in \mathcal{SRE}$ has attributes: id, date, duration, improvement\_actions, team\_satisfaction, moderation.
    \item $\mathcal{SBL}$: Set of Sprint Backlogs, where each $sbl \in \mathcal{SBL}$ has attributes: id, number\_of\_tasks, last\_updated, status, total\_effort.
    \item $\mathcal{SG}$: Set of Sprint Goals, where each $sg \in \mathcal{SG}$ has attributes: id, objective\_description, achievement\_status, benefit.
    \item $\mathcal{E}$: Set of Epics, where each $e \in \mathcal{E}$ has attributes: id, title, description, priority, status, estimated\_effort.
    \item $\mathcal{US}$: Set of User Stories, where each $us \in \mathcal{US}$ has attributes: id, title, description, acceptance\_criteria, priority, story\_points, status.
    \item $\mathcal{TSK}$: Set of Tasks, where each $tsk \in \mathcal{TSK}$ has attributes: id, title, description, status, effort, type.
    \item $\mathcal{DEV}$: Set of Development Snapshots, where each $dev \in \mathcal{DEV}$ has attributes: id, version\_number, creation\_date, test\_status, deployment\_target, documentation.
    \item $\mathcal{BL}$: Set of Blockers, where each $bl \in \mathcal{BL}$ has attributes: id, title, description, severity, status, detected\_on, resolved\_on.
    \item $\mathcal{SH}$: Set of Stakeholders, where each $sh \in \mathcal{SH}$ has attributes: id, name, organization, role, email, area\_of\_interest, influence\_level, relevance\_to\_feature.
    \item $\mathcal{VEL}$: Set of Velocity Records, where each $vel \in \mathcal{VEL}$ has attributes: id, number\_of\_sprints\_used, avg.\_story\_points, max\_velocity, min\_velocity, trend.
    \item $\mathcal{REP}$: Set of Release Plans, where each $rep \in \mathcal{REP}$ has attributes: id, version, planned\_date, included\_features, status.
    \item $\mathcal{RM}$: Set of Roadmaps, where each $rm \in \mathcal{RM}$ has attributes: id, start\_date, end\_date, milestones, objectives, versions.
    \item $\mathcal{SCB}$: Set of Scrum Boards, where each $scb \in \mathcal{SCB}$ has attributes: id, board\_type, columns\_(todo/done...), number\_of\_cards, last\_updated.
    \item $\mathcal{FED}$: Set of Feature Documentations, where each $fed \in \mathcal{FED}$ has attributes: id, title, description, creation\_date, change\_log, linked\_requirements, author.

\section{2. Indices}

\item $p \in \mathcal{P}$: Index over projects.
    \item $t \in \mathcal{T}$: Index over teams.
    \item $w \in \mathcal{W}$: Index over workers.
    \item $f \in \mathcal{F}$: Index over features.
    \item $s \in \mathcal{S}$: Index over skills.
    \item $r \in \mathcal{R}$: Index over roles.
    \item $sp \in \mathcal{SP}$: Index over sprints.
    \item $us \in \mathcal{US}$: Index over user stories.
    \item $tsk \in \mathcal{TSK}$: Index over tasks.
    \item $bl \in \mathcal{BL}$: Index over blockers.
    \item $sh \in \mathcal{SH}$: Index over stakeholders.
    \item $vel \in \mathcal{VEL}$: Index over velocity records.
    \item $rep \in \mathcal{REP}$: Index over release plans.
    \item $rm \in \mathcal{RM}$: Index over roadmaps.

\section{3. Goals}

Each goal is defined with its identifier, name, and mathematical/logical formulation. Let $w_g$ denote the weight of goal $g$.

\item[G0] \texttt{maximize\_project\_budget}: Maximize total project budget.
    \[
    \max \sum_{p \in \mathcal{P}} w_{G0} \cdot \text{budget}(p)
    \]

    \item[G1] \texttt{maximize\_team\_size}: Maximize total team size.
    \[
    \max \sum_{t \in \mathcal{T}} w_{G1} \cdot \text{team\_size}(t)
    \]

    \item[G2] \texttt{maximize\_worker\_availability}: Maximize sum of worker availability.
    \[
    \max \sum_{w \in \mathcal{W}} w_{G2} \cdot \text{availability}(w)
    \]

    \item[G3] \texttt{minimize\_project\_duration}: Minimize total project duration.
    \[
    \min \sum_{p \in \mathcal{P}} w_{G3} \cdot (\text{project\_end}(p) - \text{project\_start}(p))
    \]

    \item[G4] \texttt{maximize\_feature\_priority}: Maximize sum of feature priorities.
    \[
    \max \sum_{f \in \mathcal{F}} w_{G4} \cdot \text{priority}(f)
    \]

    \item[G5] \texttt{maximize\_story\_points}: Maximize completed story points.
    \[
    \max \sum_{us \in \mathcal{US}} w_{G5} \cdot \text{story\_points}(us)
    \]

    \item[G6] \texttt{minimize\_task\_effort}: Minimize total task effort.
    \[
    \min \sum_{tsk \in \mathcal{TSK}} w_{G6} \cdot \text{effort}(tsk)
    \]

    \item[G7] \texttt{maximize\_sprint\_achievement}: Maximize average sprint goal achievement.
    \[
    \max \frac{1}{|\mathcal{SP}|} \sum_{sp \in \mathcal{SP}} w_{G7} \cdot \text{achievement\_of\_goal}(sp)
    \]

    \item[G8] \texttt{maximize\_velocity\_trend}: Maximize positive trend in velocity.
    \[
    \max \sum_{vel \in \mathcal{VEL}} w_{G8} \cdot \text{trend}(vel)
    \]

    \item[G9] \texttt{minimize\_blocker\_severity}: Minimize total blocker severity.
    \[
    \min \sum_{bl \in \mathcal{BL}} w_{G9} \cdot \text{severity}(bl)
    \]

    \item[G10] \texttt{maximize\_stakeholder\_influence}: Maximize influence of engaged stakeholders.
    \[
    \max \sum_{sh \in \mathcal{SH}} w_{G10} \cdot \text{influence\_level}(sh)
    \]

    \item[G11] \texttt{maximize\_documentation\_coverage}: Maximize number of documented features.
    \[
    \max \sum_{fed \in \mathcal{FED}} w_{G11} \cdot \mathbb{I}[\text{linked\_requirements}(fed) \neq \emptyset]
    \]

    \item[G12] \texttt{minimize\_sprint\_duration}: Minimize total sprint duration.
    \[
    \min \sum_{sp \in \mathcal{SP}} w_{G12} \cdot (\text{end\_date}(sp) - \text{start\_date}(sp))
    \]

    \item[G13] \texttt{maximize\_release\_inclusion}: Maximize features included in releases.
    \[
    \max \sum_{rep \in \mathcal{REP}} w_{G13} \cdot |\text{included\_features}(rep)|
    \]

    \item[G14] \texttt{maximize\_epic\_effort\_estimate}: Maximize estimated effort of epics.
    \[
    \max \sum_{e \in \mathcal{E}} w_{G14} \cdot \text{estimated\_effort}(e)
    \]

\section{4. Conditions}

Each condition is a constraint with logical formulation. Let $c$ denote the condition ID.

\item[C0] \texttt{require\_project\_status}: Only active or completed projects are valid.
    \[
    \forall p \in \mathcal{P}: \text{status}(p) \in \{\text{active}, \text{completed}\}
    \]

    \item[C1] \texttt{require\_team\_location}: Teams must be in allowed locations.
    \[
    \forall t \in \mathcal{T}: \text{location}(t) \in L_{\text{allowed}}
    \]
    where $L_{\text{allowed}}$ is a predefined set of acceptable locations.

    \item[C2] \texttt{require\_worker\_status}: Only active workers are eligible.
    \[
    \forall w \in \mathcal{W}: \text{status}(w) = \text{active}
    \]

    \item[C3] \texttt{require\_feature\_status}: Only approved features can be scheduled.
    \[
    \forall f \in \mathcal{F}: \text{status}(f) = \text{approved}
    \]

    \item[C4] \texttt{require\_task\_status}: Only todo or in-progress tasks are considered.
    \[
    \forall tsk \in \mathcal{TSK}: \text{status}(tsk) \in \{\text{todo}, \text{in\_progress}\}
    \]

    \item[C5] \texttt{require\_role\_certification}: Only certified roles are assigned.
    \[
    \forall r \in \mathcal{R}: \text{description}(r) \text{ must imply certification}
    \]

    \item[C6] \texttt{require\_user\_story\_status}: Only ready or accepted user stories are valid.
    \[
    \forall us \in \mathcal{US}: \text{status}(us) \in \{\text{ready}, \text{accepted}\}
    \]

    \item[C7] \texttt{require\_sprint\_status}: Only planned or active sprints are valid.
    \[
    \forall sp \in \mathcal{SP}: \text{status}(sp) \in \{\text{planned}, \text{active}\}
    \]

    \item[C8] \texttt{require\_blocker\_status}: Active blockers must be resolved before sprint end.
    \[
    \forall bl \in \mathcal{BL}: \text{status}(bl) = \text{resolved} \vee \text{resolved\_on}(bl) < \text{end\_date}(\text{sprint}(bl))
    \]

    \item[C9] \texttt{require\_velocity\_min\_value}: Minimum velocity threshold.
    \[
    \forall vel \in \mathcal{VEL}: \text{min\_velocity}(vel) \geq V_{\min}
    \]
    where $V_{\min}$ is a given threshold.

    \item[C10] \texttt{require\_stakeholder\_relevance}: Stakeholders must have medium or high relevance.
    \[
    \forall sh \in \mathcal{SH}: \text{relevance\_to\_feature}(sh) \in \{\text{medium}, \text{high}\}
    \]

    \item[C11] \texttt{require\_skill\_certified}: Only certified skills are used.
    \[
    \forall s \in \mathcal{S}: \text{certified}(s) = \text{true}
    \]

    \item[C12] \texttt{require\_documentation\_author}: Documentation must have an author.
    \[
    \forall fed \in \mathcal{FED}: \text{author}(fed) \neq \text{null}
    \]

    \item[C13] \texttt{require\_scumb\_board\_type}: Only digital scrum boards allowed.
    \[
    \forall scb \in \mathcal{SCB}: \text{board\_type}(scb) = \text{digital}
    \]

    \item[C14] \texttt{require\_development\_test\_status}: Only tested snapshots are deployable.
    \[
    \forall dev \in \mathcal{DEV}: \text{test\_status}(dev) = \text{tested}
    \]

\section{5. Decision Variables}

\item[DV0] $\omega_p \in \{0.0, 0.5, 1.0, 1.5, 2.0\}$: Project priority weight for $p \in \mathcal{P}$.
    \item[DV1] $u_t \in [0.0, 1.0]$: Team $t$'s capacity utilization rate.
    \item[DV2] $x_{w,tsk} \in \{0,1\}$: Binary variable indicating if worker $w$ is assigned to task $tsk$.
    \item[DV3] $y_{us} \in \{0,1\}$: Binary variable indicating if user story $us$ is included in current sprint.
    \item[DV4] $z_f \in \{0,1\}$: Binary variable indicating if feature $f$ is included in next release.
    \item[DV5] $a_w \in [0, 40]$: Weekly availability (hours) of worker $w$.
    \item[DV6] $sp_{us} \in \{1,2,3,5,8,13\}$: Estimated story points for user story $us$.
    \item[DV7] $e_{tsk} \in [1, 100]$: Effort (hours) allocated to task $tsk$.
    \item[DV8] $d_{bl} \in [1, 30]$: Estimated resolution time (days) for blocker $bl$.
    \item[DV9] $c_{fed} \in [0.0, 1.0]$: Completeness score of feature documentation $fed$.
    \item[DV10] $g_{sp} \in [0.0, 1.0]$: Achievement score of sprint $sp$'s goal.
    \item[DV11] $v_{\text{next}} \in [0, 100.0]$: Predicted velocity for next sprint.
    \item[DV12] $\delta_r \in [-30, 30]$: Deviation in days from planned release date $r$.
    \item[DV13] $i_{sre} \in [0, 20]$ Number of improvement actions from retrospective $sre$.
    \item[DV14] $col_{tsk} \in \{0,1,2,3\}$: Column index of task $tsk$ on scrum board.

\end{document}