\documentclass[11pt,a4paper]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{SCRUM Domain Optimization Model}
\author{Generated from Entities, Relationships, Goals, Conditions, Decision Variables}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\newpage

% -----------------------------------------------------------------------------
\section{1. Sets (Entities)}
\begin{itemize}[leftmargin=2em]
  \item $\mathcal{P}$: Projects (\texttt{Project})
  \item $\mathcal{T}$: Teams (\texttt{Team})
  \item $\mathcal{W}$: Workers (\texttt{Worker})
  \item $\mathcal{F}$: Features (\texttt{Feature})
  \item $\mathcal{S\!K}$: Skills (\texttt{Skill})
  \item $\mathcal{R\!O}$: Roles (\texttt{Role})
  \item $\mathcal{P\!O}$: Product Owners (\texttt{ProductOwner})
  \item $\mathcal{S\!M}$: Scrum Masters (\texttt{ScrumMaster})
  \item $\mathcal{P\!B}$: Product Backlogs (\texttt{ProductBacklog})
  \item $\mathcal{S\!P}$: Sprints (\texttt{Sprint})
  \item $\mathcal{S\!PP}$: Sprint Plannings (\texttt{SprintPlanning})
  \item $\mathcal{D\!S}$: Daily Scrums (\texttt{DailyScrum})
  \item $\mathcal{S\!R}$: Sprint Reviews (\texttt{SprintReview})
  \item $\mathcal{S\!RE}$: Sprint Retrospectives (\texttt{SprintRetrospective})
  \item $\mathcal{S\!BL}$: Sprint Backlogs (\texttt{SprintBacklog})
  \item $\mathcal{S\!G}$: Sprint Goals (\texttt{SprintGoal})
  \item $\mathcal{E}$: Epics (\texttt{Epic})
  \item $\mathcal{U\!S}$: User Stories (\texttt{UserStory})
  \item $\mathcal{T\!S\!K}$: Tasks (\texttt{Task})
  \item $\mathcal{D\!E\!V}$: Development Snapshots (\texttt{DevelopmentSnapshot})
  \item $\mathcal{B\!L}$: Blockers (\texttt{Blocker})
  \item $\mathcal{S\!H}$: Stakeholders (\texttt{Stakeholder})
  \item $\mathcal{V\!E\!L}$: Velocity records (\texttt{Velocity})
  \item $\mathcal{R\!E\!P}$: Release Plans (\texttt{ReleasePlan})
  \item $\mathcal{R\!M}$: Roadmaps (\texttt{Roadmap})
  \item $\mathcal{S\!C\!B}$: Scrum Boards (\texttt{ScrumBoard})
  \item $\mathcal{F\!E\!D}$: Feature Docs (\texttt{FeatureDocumentation})
\end{itemize}

\paragraph{Relationship-induced index sets (from \texttt{Relationships.csv}).} We use the following incidence sets:
\begin{itemize}[leftmargin=2em]
  \item $\mathcal{T}(p)\subseteq\mathcal{T}$: teams assigned to project $p$ (R1).
  \item $\mathcal{W}(t)\subseteq\mathcal{W}$: workers belonging to team $t$ (R2).
  \item $\mathcal{S\!K}(w)\subseteq\mathcal{S\!K}$: skills of worker $w$ (R3).
  \item $\mathcal{R\!O}(w)\subseteq\mathcal{R\!O}$: roles of worker $w$ (R4).
  \item $\mathcal{F}(pb)\subseteq\mathcal{F}$: features contained in product backlog $pb$ (R7).
  \item $\mathcal{E}(pb)\subseteq\mathcal{E}$: epics in product backlog (R8).
  \item $\mathcal{U\!S}(e)\subseteq\mathcal{U\!S}$: user stories in epic $e$ (R9).
  \item $\mathcal{T\!S\!K}(us)\subseteq\mathcal{T\!S\!K}$: tasks in user story $us$ (R10).
  \item $\mathcal{U\!S}(\,sbl\,)\subseteq\mathcal{U\!S}$: stories assigned to sprint backlog $sbl$ (R11).
  \item $sbl(s)\in\mathcal{S\!B\!L}$: unique sprint backlog of sprint $s$ (R12).
  \item $sg(s)\in\mathcal{S\!G}$: goal of sprint $s$ (R13).
  \item $\mathcal{T\!S\!K}(scb)\subseteq\mathcal{T\!S\!K}$: tasks on scrum board $scb$ (R14).
  \item $f(FED)\in\mathcal{F}$: feature documented by a feature doc (R15).
  \item $\mathcal{B\!L}(tsk)\subseteq\mathcal{B\!L}$: blockers of task $tsk$ (R16).
  \item $\mathcal{S\!R}(sh)\subseteq\mathcal{S\!R}$: reviews a stakeholder attends (R17).
  \item $\mathcal{S\!RE}(sm)\subseteq\mathcal{S\!RE}$: retros moderated by scrum master $sm$ (R18).
  \item $t(vel)\in\mathcal{T}$: team referred to by velocity record (R19).
  \item $\mathcal{F}(rep)\subseteq\mathcal{F}$: features planned in release plan (R20).
  \item $rm(rep)\in\mathcal{R\!M}$: roadmap of release plan (R21).
  \item $dev(s)\in\mathcal{D\!E\!V}$: snapshot generated by sprint $s$ (R22).
\end{itemize}

% -----------------------------------------------------------------------------
\section{2. Indices}
\begin{itemize}[leftmargin=2em]
  \item $p\in\mathcal{P}$, $t\in\mathcal{T}$, $w\in\mathcal{W}$, $f\in\mathcal{F}$, $sk\in\mathcal{S\!K}$, $ro\in\mathcal{R\!O}$
  \item $po\in\mathcal{P\!O}$, $sm\in\mathcal{S\!M}$, $pb\in\mathcal{P\!B}$, $s\in\mathcal{S\!P}$, $spp\in\mathcal{S\!PP}$
  \item $ds\in\mathcal{D\!S}$, $sr\in\mathcal{S\!R}$, $sre\in\mathcal{S\!RE}$, $sbl\in\mathcal{S\!B\!L}$, $sg\in\mathcal{S\!G}$
  \item $e\in\mathcal{E}$, $us\in\mathcal{U\!S}$, $tsk\in\mathcal{T\!S\!K}$, $dev\in\mathcal{D\!E\!V}$, $bl\in\mathcal{B\!L}$
  \item $sh\in\mathcal{S\!H}$, $vel\in\mathcal{V\!E\!L}$, $rep\in\mathcal{R\!E\!P}$, $rm\in\mathcal{R\!M}$, $scb\in\mathcal{S\!C\!B}$
\end{itemize}

\paragraph{Selected parameters (from attributes).} We use numeric parameters derived from entity attributes:
\begin{itemize}[leftmargin=2em]
  \item $budget_p\ge 0$ (\texttt{Project.budget}); $status^\text{active}_p\in\{0,1\}$ (\texttt{Project.status=active})
  \item $avail_w\in[0,1]$ (\texttt{Worker.availability}); $status^\text{active}_w\in\{0,1\}$
  \item $teamstat^\text{available}_t\in\{0,1\}$; $size^{\min},size^{\max}$ bounds for team size
  \item $prio_f\in\mathbb{Z}_{+}$; $\widehat{eff}_f\ge 0$ (\texttt{Feature.estimated\_effort})
  \item $sev_{bl}\in\mathbb{Z}_{+}$; $resolved_{bl}\in\{0,1\}$
  \item $att_{sr}\in\mathbb{Z}_{+}$ (\texttt{SprintReview.attendees\_count})
  \item $goalAch_s\in[0,1]$ (\texttt{Sprint.achievement\_of\_goal})
  \item $vel^{avg}_{vel}\ge 0$ and mapping $t(vel)$ (\texttt{Velocity.avg\_story\_points})
  \item $totEff_{sbl}\ge 0$, $nTasks_{sbl}\in\mathbb{Z}_{+}$ (\texttt{SprintBacklog})
  \item $rel_{sh}\in[0,1]$ (\texttt{Stakeholder.relevance\_to\_feature})
\end{itemize}

% -----------------------------------------------------------------------------
\section{3. Goals}
We maximize a weighted sum of \emph{maximize\_...} terms and minimize a weighted sum of \emph{minimize\_...} terms by converting minimization components to maximization (via subtraction from upper bounds or negation). Let $\lambda_g>0$ denote the CSV weight of goal $g$ and $\mathrm{Norm}[\cdot]$ a positive scaling to place heterogeneous terms on comparable ranges.

\begin{itemize}[leftmargin=2em]

  \item \textbf{G0 \; maximize\_avg\_story\_points} (Weight $1.0$, CriteriaType $1$)\\
  \emph{Logic:} Prefer teams with higher historical velocity.\\
  \emph{Math:} $\displaystyle \max \; \lambda_{G0}\sum_{vel\in\mathcal{V\!E\!L}}\mathrm{Norm}\big[vel^{avg}_{vel}\big]$

  \item \textbf{G1 \; minimize\_blocker\_severity} (Weight $1.0$, CriteriaType $2$)\\
  \emph{Logic:} Reduce unresolved blocker impact.\\
  \emph{Math:} $\displaystyle \min \; \lambda_{G1}\sum_{tsk\in\mathcal{T\!S\!K}}\sum_{bl\in\mathcal{B\!L}(tsk)}(1-resolved_{bl})\;sev_{bl}$

  \item \textbf{G2 \; minimize\_task\_effort} (Weight $0.9$, CriteriaType $1$)\\
  \emph{Logic:} Prefer selecting/assigning lower-effort tasks. Let $a_{tsk,w}\in\{0,1\}$ (DV4).\\
  \emph{Math:} $\displaystyle \min \; \lambda_{G2}\sum_{tsk}\sum_{w} a_{tsk,w}\;effort_{tsk}$

  \item \textbf{G3 \; maximize\_sprint\_goal\_achievement} (Weight $1.0$, CriteriaType $2$)\\
  \emph{Logic:} Favor sprints with higher goal achievement.\\
  \emph{Math:} $\displaystyle \max \; \lambda_{G3}\sum_{s\in\mathcal{S\!P}}\mathrm{Norm}\big[goalAch_s\big]$

  \item \textbf{G4 \; minimize\_feature\_estimated\_effort} (Weight $0.8$, CriteriaType $1$)\\
  \emph{Logic:} Prefer lower-effort features when selected for a sprint. Let $y_{f,s}\in\{0,1\}$ (DV2 adapted over sprints).\\
  \emph{Math:} $\displaystyle \min \; \lambda_{G4}\sum_{s}\sum_{f} y_{f,s}\;\widehat{eff}_f$

  \item \textbf{G5 \; maximize\_stakeholder\_relevance} (Weight $0.7$, CriteriaType $1$)\\
  \emph{Logic:} Prefer items valuable to highly relevant stakeholders. Map features to stakeholders by participation in reviews of sprints that include those features.\\
  \emph{Math (proxy):} $\displaystyle \max \; \lambda_{G5}\sum_{s}\sum_{f} y_{f,s}\Big(\sum_{sr\in\mathcal{S\!R}}\sum_{sh\in\mathcal{S\!H}} \mathbf{1}[sr\in \mathcal{S\!R}(sh)]\;rel_{sh}\Big)$

  \item \textbf{G6 \; minimize\_total\_sprint\_effort} (Weight $1.0$, CriteriaType $2$)\\
  \emph{Logic:} Keep planned effort within capacity.\\
  \emph{Math:} $\displaystyle \min \; \lambda_{G6}\sum_{s}\; totEff_{\,sbl(s)}$

  \item \textbf{G7 \; maximize\_attendees\_in\_review} (Weight $0.5$, CriteriaType $1$)\\
  \emph{Logic:} Prefer sprints with broader review participation.\\
  \emph{Math:} $\displaystyle \max \; \lambda_{G7}\sum_{sr\in\mathcal{S\!R}} \mathrm{Norm}[att_{sr}]$

  \item \textbf{G8 \; minimize\_number\_of\_tasks} (Weight $0.6$, CriteriaType $1$)\\
  \emph{Logic:} Prefer smaller WIP.\\
  \emph{Math:} $\displaystyle \min \; \lambda_{G8}\sum_{s} nTasks_{\,sbl(s)}$

  \item \textbf{G9 \; maximize\_worker\_availability} (Weight $1.0$, CriteriaType $2$)\\
  \emph{Logic:} Assign work to more-available workers.\\
  \emph{Math:} $\displaystyle \max \; \lambda_{G9}\sum_{tsk}\sum_{w} a_{tsk,w}\; \mathrm{Norm}[avail_w]$

  \item \textbf{G10 \; minimize\_project\_budget} (Weight $0.9$, CriteriaType $1$)\\
  \emph{Logic:} Prefer plans consuming less budget. If $b_f\ge 0$ is allocated feature budget (DV8), assign features to projects by backlog.\\
  \emph{Math:} $\displaystyle \min \; \lambda_{G10}\sum_{p\in\mathcal{P}} \sum_{pb:\,pb\text{ of }p}\sum_{f\in\mathcal{F}(pb)} b_f \le \sum_{p} budget_p\quad\text{(also enforced as constraint in Sec.\;4)}$

  \item \textbf{G11 \; maximize\_scrum\_master\_experience} (Weight $0.4$, CriteriaType $1$)\\
  \emph{Logic:} Prefer assigning more-experienced SMs. Let $z_{sm,t}\in\{0,1\}$ (DV5). Parameter $exp_{sm}\ge 0$.\\
  \emph{Math:} $\displaystyle \max \; \lambda_{G11}\sum_{t\in\mathcal{T}}\sum_{sm\in\mathcal{S\!M}} z_{sm,t}\;\mathrm{Norm}[exp_{sm}]$
\end{itemize}

\paragraph{Composite objective.} With $\mathcal{G}_{\max}$ the set of maximize-goals and $\mathcal{G}_{\min}$ minimize-goals (converted by sign/upper bounds), we solve:
\[
\max \;\; \sum_{g\in\mathcal{G}_{\max}} \lambda_g \cdot \text{Term}_g \;\; - \sum_{g\in\mathcal{G}_{\min}} \lambda_g \cdot \text{Term}_g^{(\min)}
\]
subject to the conditions in Section~4 and variable domains in Section~5.

% -----------------------------------------------------------------------------
\section{4. Conditions}
\textbf{Interpretation rule:} For each condition $Ck$, CriteriaType $=2$ (\emph{Must-Match}) is a hard constraint; $=1$ (\emph{May-Match}) is modeled as a soft preference added to the objective (positive bonus or negative penalty); $=0$ (\emph{Cannot-Match}) forbids assignments/selections.

Let further decision variables from Sec.\;5 be available. We list each condition with logic and mathematics.

\begin{itemize}[leftmargin=2em]

  \item \textbf{C0 \; active\_projects\_only} (Must, IsSum=False)\\
  \emph{Logic:} Only active projects participate.\\
  \emph{Math:} $\forall p\in\mathcal{P}: \; status^\text{active}_p=1$ (or equivalently, filter $\mathcal{P}\leftarrow\{p:status^\text{active}_p=1\}$).

  \item \textbf{C1 \; team\_status\_available} (Must)\\
  \emph{Logic:} Only available teams can be used.\\
  \emph{Math:} $\forall t\in\mathcal{T}: \; teamstat^\text{available}_t=1$.

  \item \textbf{C2 \; worker\_status\_active} (Must)\\
  \emph{Logic:} Only active workers can be assigned.\\
  \emph{Math:} $\forall w\in\mathcal{W},\forall t:\; x_{w,t}\le status^\text{active}_w,\;\forall p:\; u_{w,p}\le status^\text{active}_w$.

  \item \textbf{C3 \; min\_worker\_availability} (Must)\\
  \emph{Logic:} Assignments require $avail_w\ge \alpha$ (threshold).\\
  \emph{Math:} $\forall w, t:\; x_{w,t}\le \mathbf{1}[avail_w\ge \alpha]$, and $\forall w,tsk:\; a_{tsk,w}\le \mathbf{1}[avail_w\ge \alpha]$.

  \item \textbf{C4 \; user\_story\_ready} (Must)\\
  \emph{Logic:} Only \emph{ready} user stories may be selected into a sprint. Let $\texttt{ready}_{us}\in\{0,1\}$.\\
  \emph{Math:} $\forall s,us:\; y^{US}_{us,s}\le \texttt{ready}_{us}$.

  \item \textbf{C5 \; feature\_priority\_threshold} (Must)\\
  \emph{Logic:} Selected features must have $prio_f\ge \underline{\pi}$.\\
  \emph{Math:} $\forall s,f:\; y_{f,s}\le \mathbf{1}[\,\prio_f\ge \underline{\pi}\,]$.

  \item \textbf{C6 \; sprint\_in\_progress\_or\_planned} (Must)\\
  \emph{Logic:} Consider only sprints with admissible status. Let $\texttt{ok}_s\in\{0,1\}$.\\
  \emph{Math:} $\forall s:\; \texttt{ok}_s=1$ (or restrict $\mathcal{S\!P}$ accordingly).

  \item \textbf{C7 \; exclude\_unresolved\_blockers} (Cannot-Match, IsSum=True)\\
  \emph{Logic:} Tasks with unresolved blockers cannot be assigned.\\
  \emph{Math:} $\forall tsk,\forall bl\in\mathcal{B\!L}(tsk):\; (1-resolved_{bl})=1 \Rightarrow \sum_{w} a_{tsk,w}=0$.

  \item \textbf{C8 \; prefer\_dev\_task\_type} (May-Match)\\
  \emph{Logic:} Prefer \texttt{Task.type=development}. Let $\texttt{dev}_{tsk}\in\{0,1\}$. Weight $0.5$.\\
  \emph{Math (objective bonus):} $+\;0.5\sum_{tsk,w} a_{tsk,w}\cdot \texttt{dev}_{tsk}$.

  \item \textbf{C9 \; backlog\_status\_refined} (Must)\\
  \emph{Logic:} Only refined product backlogs contribute features/stories. Let $\texttt{refined}_{pb}\in\{0,1\}$.\\
  \emph{Math:} $\forall pb:\; \texttt{refined}_{pb}=1$ and for $f\in\mathcal{F}(pb)$ or $us\in\mathcal{U\!S}(e), e\in\mathcal{E}(pb)$, selections must satisfy $y_{f,s}\le \texttt{refined}_{pb}$ and $y^{US}_{us,s}\le \texttt{refined}_{pb}$.

  \item \textbf{C10 \; release\_plan\_planned} (Must)\\
  \emph{Logic:} Only planned release plans are considered. Let $\texttt{planned}_{rep}\in\{0,1\}$.\\
  \emph{Math:} $\forall rep:\; \texttt{planned}_{rep}=1$.

  \item \textbf{C11 \; roadmap\_end\_date\_defined} (Must)\\
  \emph{Logic:} Roadmaps must have end date set. Let $\texttt{hasEnd}_{rm}\in\{0,1\}$.\\
  \emph{Math:} $\forall rep:\; \texttt{hasEnd}_{rm(rep)}=1$.
\end{itemize}

\paragraph{Capacity, budget, and linking (implied by entities/relationships).}
\begin{itemize}[leftmargin=2em]
  \item \emph{Worker--Team assignment (DV0):} $x_{w,t}\in\{0,1\}$ and $\sum_{t}x_{w,t}\le 1$.
  \item \emph{Worker--Project assignment (DV1):} $u_{w,p}\in\{0,1\}$ and $u_{w,p}\le \sum_{t\in\mathcal{T}(p)} x_{w,t}$ (project via team).
  \item \emph{ScrumMaster--Team (DV5):} $z_{sm,t}\in\{0,1\}$ and $\sum_{sm} z_{sm,t}=1$.
  \item \emph{ProductOwner--Project (DV6):} $q_{po,p}\in\{0,1\}$ and $\sum_{po} q_{po,p}=1$.
  \item \emph{Feature--Sprint selection (DV2):} $y_{f,s}\in\{0,1\}$; if $f\in\mathcal{F}(pb)$ associated to project $p$, then $y_{f,s}\le \sum_{po} q_{po,p}$.
  \item \emph{Story--Sprint selection (DV3):} $y^{US}_{us,s}\in\{0,1\}$ with $us\in\mathcal{U\!S}(e)$ and (optionally) $y^{US}_{us,s}\le \sum_{f\in\mathcal{F}(pb)} y_{f,s}$ if stories are gated by chosen features/epics.
  \item \emph{Task assignment (DV4):} $a_{tsk,w}\in\{0,1\}$ and $\sum_{w} a_{tsk,w}\le 1$; link to stories $tsk\in\mathcal{T\!S\!K}(us)$ implies $a_{tsk,w}\le \sum_{s} y^{US}_{us,s}$.
  \item \emph{Sprint effort vs availability:} $\sum_{us}y^{US}_{us,s}\cdot \texttt{SP}_{us}\le \sum_{w} cap_{w,s}$ where $\texttt{SP}_{us}$ are (DV11) story points and $cap_{w,s} = avail_w\cdot Cap^{\max}$.
  \item \emph{Budget (DV8, G10):} $\sum_{f} b_f \le \sum_{p} budget_p$ and $b_f \le M\sum_{s} y_{f,s}$.
  \item \emph{Team size (DV9):} $size^{\min}\le n_t \le size^{\max}$ with $n_t=\sum_{w} x_{w,t}$.
  \item \emph{Sprint length (DV7):} $7\le L_s \le 30$ (days).
  \item \emph{Feature priority (DV10):} $1\le \pi_f \le 5$ and if $y_{f,s}=1$ then $\pi_f\ge \underline{\pi}$ (duplicate of C5).
\end{itemize}

% -----------------------------------------------------------------------------
\section{5. DecisionVariables}
Let the following decision variables correspond exactly to \texttt{DecisionVariables.csv} (domains and bounds included).

\begin{itemize}[leftmargin=2em]
  \item \textbf{DV0 \; assign\_worker\_to\_team}:
  $x_{w,t}\in\{0,1\}$, $w\in\mathcal{W}, t\in\mathcal{T}$ (1 if worker $w$ is assigned to team $t$).
  \item \textbf{DV1 \; assign\_worker\_to\_project}:
  $u_{w,p}\in\{0,1\}$, $w\in\mathcal{W}, p\in\mathcal{P}$ (1 if worker $w$ contributes to project $p$).
  \item \textbf{DV2 \; select\_feature\_for\_sprint}:
  $y_{f,s}\in\{0,1\}$, $f\in\mathcal{F}, s\in\mathcal{S\!P}$ (1 if feature $f$ is in sprint $s$).
  \item \textbf{DV3 \; select\_user\_story\_for\_sprint}:
  $y^{US}_{us,s}\in\{0,1\}$, $us\in\mathcal{U\!S}, s\in\mathcal{S\!P}$.
  \item \textbf{DV4 \; assign\_task\_to\_worker}:
  $a_{tsk,w}\in\{0,1\}$, $tsk\in\mathcal{T\!S\!K}, w\in\mathcal{W}$.
  \item \textbf{DV5 \; choose\_scrum\_master\_for\_team}:
  $z_{sm,t}\in\{0,1\}$, $sm\in\mathcal{S\!M}, t\in\mathcal{T}$.
  \item \textbf{DV6 \; choose\_product\_owner\_for\_project}:
  $q_{po,p}\in\{0,1\}$, $po\in\mathcal{P\!O}, p\in\mathcal{P}$.
  \item \textbf{DV7 \; set\_sprint\_length\_days}:
  $L_s\in\mathbb{Z}$, $s\in\mathcal{S\!P}$ with $7\le L_s\le 30$.
  \item \textbf{DV8 \; allocate\_budget\_to\_feature}:
  $b_f\in\mathbb{R}_{+}$, $f\in\mathcal{F}$ with $0\le b_f\le 1{,}000{,}000$.
  \item \textbf{DV9 \; set\_team\_size}:
  $n_t\in\mathbb{Z}$, $t\in\mathcal{T}$ with $3\le n_t\le 20$.
  \item \textbf{DV10 \; set\_feature\_priority}:
  $\pi_f\in\mathbb{Z}$, $f\in\mathcal{F}$ with $1\le \pi_f\le 5$.
  \item \textbf{DV11 \; decide\_story\_points\_for\_user\_story}:
  $\texttt{SP}_{us}\in\mathbb{Z}$, $us\in\mathcal{U\!S}$ with $1\le \texttt{SP}_{us}\le 13$.
\end{itemize}

\end{document}
