\documentclass{article}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}

\title{Optimization Model for Resource Allocation}
\author{AI Assistant}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section{1. Sets (Entities)}

\begin{itemize}
    \item \textbf{Resources} ($R$):  \{$r_1$, $r_2$, $r_3$, $r_4$, $r_5$\} = \{Wood, Stone, Iron, Gold, Food\}
    \item \textbf{Projects} ($P$): \{$p_1$, $p_2$, $p_3$, $p_4$, $p_5$\} = \{House, Wall, Sword, Crown, Meal\}
    \item \textbf{Workers} ($W$): \{$w_1$, $w_2$, $w_3$, $w_4$\} = \{Alice, Bob, Charlie, David\}
\end{itemize}

\section{2. Indices}

\begin{itemize}
    \item $i$ : Index for resources, $i \in R$
    \item $j$ : Index for projects, $j \in P$
    \item $k$ : Index for workers, $k \in W$
\end{itemize}

\section{3. Goals}

\begin{itemize}
    \item \textbf{Goal ID:} G1, \textbf{Name:} Maximize Total Project Value \\
    \textbf{Mathematical Representation:} $\max \sum_{j \in P} V_j \cdot x_j$ \\
    \textbf{Logical Representation:} The model aims to maximize the total value derived from completing projects.

    \item \textbf{Goal ID:} G2, \textbf{Name:} Minimize Resource Consumption \\
    \textbf{Mathematical Representation:} $\min \sum_{i \in R} C_i \cdot y_i$ \\
    \textbf{Logical Representation:} The model aims to minimize the total cost associated with resource utilization.
\end{itemize}

\section{4. Conditions}

\begin{itemize}
    \item \textbf{Condition ID:} C1, \textbf{Name:} Resource Availability \\
    \textbf{Mathematical Representation:} $\sum_{j \in P} a_{ij} \cdot x_j \le A_i, \forall i \in R$ \\
    \textbf{Logical Representation:} The total resource consumption by all projects must not exceed the available amount of each resource.

    \item \textbf{Condition ID:} C2, \textbf{Name:} Project Completion \\
    \textbf{Mathematical Representation:} $x_j \in \{0, 1\}, \forall j \in P$ \\
    \textbf{Logical Representation:} Each project can either be completed (1) or not completed (0).

    \item \textbf{Condition ID:} C3, \textbf{Name:} Worker Assignment \\
    \textbf{Mathematical Representation:} $\sum_{j \in P} b_{jk} \cdot x_j \le 1, \forall k \in W$ \\
    \textbf{Logical Representation:}  Each worker can be assigned to at most one project.
    
    \item \textbf{Condition ID:} C4, \textbf{Name:} Project Resource Requirement \\
    \textbf{Mathematical Representation:} $\sum_{i \in R} a_{ij} \cdot x_j  = 1, \forall j \in P$ \\
    \textbf{Logical Representation:} Each project requires at least one resource to be built.

\end{itemize}

\section{5. DecisionVariables}

\begin{itemize}
    \item $x_j$: Binary variable indicating whether project $j$ is completed (1) or not (0).  $x_j \in \{0, 1\}, \forall j \in P$
    \item $y_i$:  Amount of resource $i$ consumed. $y_i \ge 0, \forall i \in R$
\end{itemize}

\end{document}